### 2016-02-04 paper.tex
Intro

\documentclass[11pt,letterpaper]{article}
\usepackage{acl2015}
\usepackage{times}

\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{mathtools}
\usepackage{dingbat}
% \usepackage{subcaption}
\usepackage{balance}
\usepackage{gensymb}
\usepackage{marginnote}
\usepackage{adjustbox}

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage{hyperref}

\sloppy

\usepackage{color}
\newcommand{\todo}[1]{}
\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}

%\renewcommand{\baselinestretch}{0.95}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\title{\ldots}

% \author{First Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain} \\\And
%   Second Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain} \\}

\date{}

\newcommand{\BASEURL}{http://example.org}
% \newcommand{\BASEURL}{https://bitbucket.org/dimazest/phd-buildout/raw/tip/notebooks/downloads/compdistmeaning}
\newcommand{\dataurl}[1]{\href{\BASEURL/#1}{\nolinkurl{#1}}}

\newcommand{\p}{\textsuperscript{\textasteriskcentered}}
\newcommand{\pw}{\textsuperscript{\dag}}

\newcommand{\pp}{\textsuperscript\dag}
\newcommand{\ppp}{\textsuperscript\ddag}
\newcommand{\np}{\phantom{\textsuperscript\textasteriskcentered}}

\def\relevant/{Relevant@3}
\def\topRR/{Top Reciprocal Rank}
\def\RR/{Reciprocal Rank}

\begin{document}
\def\emnlp/{\textit{KS2013}}
\def\PhraseRel/{PhraseRel}

\def\PMI/{$1 \operatorname{PMI}$}
\def\PPMI/{$1 \operatorname{PosPMI}$}
\def\NPMI/{$n \operatorname{PMI}$}
\def\NPPMI/{$n \operatorname{PosPMI}$}
\def\NITTF/{$n \operatorname{ITTF}$}
\def\logNPMI/{$\log n\operatorname{PMI}$}
\def\logNPPMI/{$\log n\operatorname{PosPMI}$}
\def\logNITTF/{$\log n\operatorname{ITTF}$}

\maketitle
\begin{abstract}
\input{abstract.tex}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably \emph{shifted PMI} abbreviated as \texttt{neg} and \emph{context distribution smoothing} referred to as \texttt{cds}. Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces, namely word vectors have almost 200,000 dimensions. In general, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.

Contrary to the trend of employing highly dimensional vectors, older work on lexical distributional semantics and recent work on compositional distributional semantics employ vectors with much less dimensions, for example, 2000 \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, 3000 \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or 10000 \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.

Such a mismatch in vector dimensionality selection across lexical and compositional tasks rises a number of questions this paper aims to answer.
\begin{itemize}
\item To what extent does model performance depend on vector dimensionality?
\item Do parameters influence performance of highly dimensional models the same way as lowly dimensional models? Are finding of \newcite{TACL570} directly transferred to lowly dimensional models?
\item Is it possible to come up with the heuristics for model parameter selection? If so, what are they?
\item Can the heuristics based on lexical tasks be transferred to compositional tasks?
\end{itemize}

To answer this study we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.

%\bibliographystyle{acl}
% remove publisher, month etc from conf proceedings:
\bibliographystyle{acl-short}
% \bibliographystyle{naaclhlt2016}
% \balance
\bibliography{references,dmilajevs_publications}

\end{document}

### 2016-02-04 paper.tex
Typo

@@
 
-To answer this study we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.
+To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.
 
@@
 % \bibliographystyle{naaclhlt2016}
-% \balance
+\balance
 \bibliography{references,dmilajevs_publications}

### 2016-02-04 paper.tex
Parameters

@@
 \def\PPMI/{$1 \operatorname{PosPMI}$}
+\def\CPMI/{$1 \operatorname{CPMI}$}
+\def\PCPMI/{$1 \operatorname{PCPMI}$}
+
 \def\NPMI/{$n \operatorname{PMI}$}
 \def\NPPMI/{$n \operatorname{PosPMI}$}
-\def\NITTF/{$n \operatorname{ITTF}$}
+\def\NCPMI/{$n \operatorname{CPMI}$}
+\def\NPCPMI/{$n \operatorname{PCPMI}$}
+
 \def\logNPMI/{$\log n\operatorname{PMI}$}
 \def\logNPPMI/{$\log n\operatorname{PosPMI}$}
-\def\logNITTF/{$\log n\operatorname{ITTF}$}
+\def\logNCPMI/{$\log n \operatorname{CPMI}$}
+\def\logNPCPMI/{$\log n \operatorname{PCPMI}$}
 
@@
 \newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably \emph{shifted PMI} abbreviated as \texttt{neg} and \emph{context distribution smoothing} referred to as \texttt{cds}.
-Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces, namely word vectors have almost 200,000 dimensions.
+Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces, namely word vectors have almost 200000 dimensions.
 In general, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.
@@
 
-To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714} and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.
+To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}; and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.
+
+\section{Parameters}
+\label{sec:parameters}
+
+\subsection{PMI variants (\texttt{discr})}
+\label{sec:pmi-variants}
+
+Co-occurrence weightings schemes based on \emph{Point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) have been successfully applied in distributional semantics (see for example \newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756} and \newcite{NIPS2014_5477}).
+%
+\begin{equation}
+  \label{eq:pmi}
+  \operatorname{PMI}(x, y) = \log\frac{P(x,y)}{P(x)P(y)}
+\end{equation}
+
+PMI is not directly applicable to the co-occurrence counts because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity.
+A straightforward ``fix'' to this problem is to replace all infinities with zeroes.
+Such a replacement preserve sparsity of the input co-occurrence matrix.
+Later in the paper, we use PMI to refer to a weighting with this fix.
+
+An alternative solution of avoiding infinity is to increment the probability ratio by one:
+%
+\begin{equation}
+  \label{eq:cpmi}
+  \operatorname{CPMI}(x, y) = \log\Big( 1 + \frac{P(x,y)}{P(x)P(y)} \Big)
+\end{equation}
+
+\subsection{Shifted PMI (\texttt{neg})}
+\label{sec:shifted-pmi}
+
+It has been experimentally shown that negative PMI values do not positively contribute to model performance and worth nullifying \cite{Turney:2010:FMV:1861751.1861756}.
+
+\emph{Positive PMI} (PosPMI) extended with an additional additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570} is the third PMI variant used in this work:
+%
+\begin{equation}
+  \label{eq:ppmi}
+  \operatorname{PosPMI_k} = \max (0, \operatorname{PMI}(x, y) - \log k)
+\end{equation}
+%
+As $k$ increases, more values become 0 and, consequently, vectors become sparser. $k = 1$ is equivalent to vanilla positive PMI without shifting. When $k < 1$ vectors are denser.
+
+Finally, we can apply the same idea to CPMI:
+%
+\begin{equation}
+  \label{eq:pcpmi}
+  \operatorname{PCPMI_k} = \max (0, \operatorname{CPMI}(x, y) - \log 2k)
+\end{equation}
+
+\subsection{Frequency weighting (\texttt{freq})}
+\label{sec:frequency-weighting}
+
+Another issue with PMI is its bias towards rare events \cite{TACL570} one way of solving this issue is to weight PMI value by the co-occurrence frequency \cite{Evert05}:
+%
+\begin{equation}
+  \label{eq:lmi}
+  \operatorname{LMI}(x, y) = n\operatorname{PMI}(x, y)
+\end{equation}
+%
+where $n$ is the number of times $x$ was seen together with $y$.
+For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NPPMI/ \NCPMI/ and \NPCPMI/.
+When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \PPMI/, \CPMI/ and \PCPMI/.
+
+In addition to $1$ and $n$ frequencies, we experiment with $\log n$ frequency.
+
+\subsection{Context distribution smoothing (\texttt{cds})}
+\label{sec:cont-distr-smooth}
+
+Context distribution smoothing (\texttt{cds}) is another parameter shown to influence performance of distributional models \cite{TACL570}. It smoothes the context distribution $P(x)$:
+%
+\begin{equation}
+  \label{eq:cds}
+  P_{\alpha}(x) = \frac{n(x)^{\alpha}}{\sum_{c}n(c)^{\alpha}}
+\end{equation}
+%
+We experiment with values of 1 (absence of smoothing) and 0.75.
+
+We also estimate probability of a context using the global context appearance in the corpus:
+%
+\begin{equation}
+  \label{eq:cds-nan}
+  P(x) = \frac{n(x)}{|C|}
+\end{equation}
+%
+where $|C|$ is the size of the used corpus. We refer to this case as \textit{global} context probability.
+
+\subsection{Vector dimensionality}
+\label{sec:vect-dimens}
+
+As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent nouns, verbs, adjectives and adverbs.
+All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.
+
+\subsection{Similarity metric}
+\label{sec:similarity-metric}
+
+We test a widely used cosine based similarity, as well as correlation \cite{kiela-clark:2014:CVSC}.
+
+\subsection{Compositional operator}
+\label{sec:comp-oper}
+
+For tasks that involve composition, we test the following operators: addition
+and multiplication \cite{mitchell2010composition}; Kronecker \cite{Grefenstette:2011:ETV:2140490.2140497}; Relational \cite{Grefenstette:2011:ESC:2145432.2145580}; Copy object and Copy subject \cite{Kartsaklis12aunified}; Frobenious addition, Frobenious multiplication and Frobenious outer \cite{kartsadrqpl2014}.
 

### 2016-02-04 paper.tex
A figure listing all parameters

@@
   \label{eq:lmi}
-  \operatorname{LMI}(x, y) = n\operatorname{PMI}(x, y)
+  \operatorname{LMI}(x, y) = n(x, y)\operatorname{PMI}(x, y)
 \end{equation}
 %
-where $n$ is the number of times $x$ was seen together with $y$.
+where $n(x, y)$ is the number of times $x$ was seen together with $y$.
 For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NPPMI/ \NCPMI/ and \NPCPMI/.
@@
 
-As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent nouns, verbs, adjectives and adverbs.
+As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent lemmatised nouns, verbs, adjectives and adverbs.
 All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.
@@
 
+\begin{figure*}[th]
+  \centering
+  \begin{tabular}{llr}
+    \toprule
+    % \multicolumn{2}{c}{Item} \\
+    % \cmidrule(r){1-2}
+    Parameter & Values \\
+    \midrule
+    \texttt{discr} & PMI, CPMI, PosPMI, PCPMI \\
+    \texttt{neg} & 0.5, 0.7, 1, 1.4, 2, 5 \\
+    \texttt{freq} & $1$, $n$, $\log n$ \\
+    \texttt{cds} & \textit{nan}, 1, 0.75 \\
+    Dimensionality & 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K, 50K \\
+    Similarity & cosine, correlation \\
+    \multirow{2}{*}{Compositional operator}
+              & add, mult, kron, relational,
+                copy-object, copy-subject, \\
+              & frobenious-add, frobenious-mult,
+                frobenious-outer
+    \\
+    Corpus & concatenation of ukWac and Wackypedia \\
+    Window size & 5 \\
+    \bottomrule
+  \end{tabular}
+  \caption{\textbf{Parameters and their values.}}
+\end{figure*}
+
 %\bibliographystyle{acl}

### 2016-02-07 figures/simlex-ppmi-best.tex
SPMI story

\begin{figure*}
  \centering
    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-best.pdf}

  \caption{\textbf{SPMI best configurations.}}
  \label{fig:simlex-ppmi-best}
\end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2016-02-07 figures/simlex-ppmi-interaction.tex
SPMI story

\begin{figure*}
  \centering
  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-cds.pdf}
    \caption{\textbf{Context distribution smoothing.}}
    \label{fig:simlex-ppmi-interaction-cds}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-neg.pdf}
    \caption{\textbf{Shifting.}}
    \label{fig:simlex-ppmi-interaction-neg}
  \end{subfigure}

  \caption{\textbf{SPMI.}}
  \label{fig:simlex-ppmi-interaction}
\end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2016-02-07 paper.tex
Using acl2016 template
SPMI story

--- 2016-02-04 paper.tex
@@
 \documentclass[11pt,letterpaper]{article}
-\usepackage{acl2015}
+\usepackage{acl2016}
 \usepackage{times}
@@
 \usepackage{dingbat}
-% \usepackage{subcaption}
+\usepackage{subcaption}
 \usepackage{balance}
@@
 \def\PMI/{$1 \operatorname{PMI}$}
-\def\PPMI/{$1 \operatorname{PosPMI}$}
+\def\SPMI/{$1 \operatorname{SPMI}$}
 \def\CPMI/{$1 \operatorname{CPMI}$}
-\def\PCPMI/{$1 \operatorname{PCPMI}$}
+\def\SCPMI/{$1 \operatorname{SCPMI}$}
 
 \def\NPMI/{$n \operatorname{PMI}$}
-\def\NPPMI/{$n \operatorname{PosPMI}$}
+\def\NSPMI/{$n \operatorname{SPMI}$}
 \def\NCPMI/{$n \operatorname{CPMI}$}
-\def\NPCPMI/{$n \operatorname{PCPMI}$}
+\def\NSCPMI/{$n \operatorname{SCPMI}$}
 
 \def\logNPMI/{$\log n\operatorname{PMI}$}
-\def\logNPPMI/{$\log n\operatorname{PosPMI}$}
+\def\logNSPMI/{$\log n\operatorname{SPMI}$}
 \def\logNCPMI/{$\log n \operatorname{CPMI}$}
-\def\logNPCPMI/{$\log n \operatorname{PCPMI}$}
+\def\logNSCPMI/{$\log n \operatorname{SCPMI}$}
 
@@
 
+\input{figures/parameters}
+
 \subsection{PMI variants (\texttt{discr})}
@@
 It has been experimentally shown that negative PMI values do not positively contribute to model performance and worth nullifying \cite{Turney:2010:FMV:1861751.1861756}.
-
-\emph{Positive PMI} (PosPMI) extended with an additional additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570} is the third PMI variant used in this work:
+Positive PMI extended with an additional additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570} is the third PMI variant (abbreviated as SPMI) used in this work:
 %
@@
   \label{eq:ppmi}
-  \operatorname{PosPMI_k} = \max (0, \operatorname{PMI}(x, y) - \log k)
+  \operatorname{SPMI_k} = \max (0, \operatorname{PMI}(x, y) - \log k)
 \end{equation}
 %
-As $k$ increases, more values become 0 and, consequently, vectors become sparser. $k = 1$ is equivalent to vanilla positive PMI without shifting. When $k < 1$ vectors are denser.
+As $k$ increases, more values become 0 and, consequently, vectors become sparser. Setting $k$ to 1 is equivalent to vanilla positive PMI without shifting. When $k < 1$ vectors are denser.
 
@@
   \label{eq:pcpmi}
-  \operatorname{PCPMI_k} = \max (0, \operatorname{CPMI}(x, y) - \log 2k)
+  \operatorname{SCPMI_k} = \max (0, \operatorname{CPMI}(x, y) - \log 2k)
 \end{equation}
@@
   \label{eq:lmi}
-  \operatorname{LMI}(x, y) = n\operatorname{PMI}(x, y)
+  \operatorname{LMI}(x, y) = n(x, y)\operatorname{PMI}(x, y)
 \end{equation}
 %
-where $n$ is the number of times $x$ was seen together with $y$.
-For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NPPMI/ \NCPMI/ and \NPCPMI/.
-When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \PPMI/, \CPMI/ and \PCPMI/.
+where $n(x, y)$ is the number of times $x$ was seen together with $y$.
+For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NSPMI/ \NCPMI/ and \NSCPMI/.
+When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \SPMI/, \CPMI/ and \SCPMI/.
 
@@
 
+Table~\ref{tab:parameters} list the parameters and their values used in this work.
+
+\section{Lexical experiments}
+\label{sec:lexical-experiments}
+
+\subsection{Shifted (positive) PMI performance}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
+  \caption{\textbf{Shifted PMI mean performance and variance.}}
+  \label{fig:ppmi-performance}
+\end{figure*}
+
+We start with exploring the performance of SPMI, in particular \SPMI/.
+Figure~\ref{fig:ppmi-performance} shows the mean performance and the variance of the SPMI models grouped by vector dimensionality and frequency on the SimLex-999 dataset.
+
+Average \SPMI/ performance increases for the dimensionality values in the range of 1K to 10K.
+After 10K dimensions, the average \SPMI/ performance degrades.
+\SPMI/ variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards.
+This suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
+
+Interestingly, \logNSPMI/ mean performance increases and variance decreases as dimensionality increases showing that this weighting is not sensitive to the parameter selection for highly dimensional models.
+
+\paragraph{Parameter interaction}
+
+Figure~\ref{fig:simlex-ppmi-interaction} shows that 10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection.
+For models with dimensionality greater than 10K, context distribution smoothing should be used with $\alpha = 0.75$.
+For models with dimensionality lower than 10K, it is beneficial to use global context probabilities.
+Shifting also depends on the dimensionality, models with up to 3K dimensions should set $k = 0.5$, models with up to 20k dimensions should set $k = 1.4$ and models with a higher number of dimensions should set $k = 5$.
+
+\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 10K.
+For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$.
+Shifting should be applied with $\alpha = 0.5$ for models with less than 10K dimensions and $\alpha = 1.4$ for models with more than 10K dimensions.
+
+\input{figures/simlex-ppmi-interaction}
+
+\input{figures/simlex-ppmi-best}
+
 %\bibliographystyle{acl}

### 2016-02-08 figures/simlex-ppmi-best.tex
Complete the section on lexical tasks.

@@
   \centering
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-best.pdf}
+  \begin{subfigure}[b]{\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-ppmi-best.pdf}
+    \caption{SimLex-999}
+    \label{fig:simlex-ppmi-best-simlex}
+  \end{subfigure}
 
-  \caption{\textbf{SPMI best configurations.}}
+  \begin{subfigure}[b]{\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/men-ppmi-best.pdf}
+    \caption{MEN}
+    \label{fig:simlex-ppmi-best-men}
+  \end{subfigure}
+
+  \caption{\textbf{SPMI best configurations.} Black line shows the best results reported by \protect\newcite{TACL570}.}
   \label{fig:simlex-ppmi-best}

### 2016-02-08 paper.tex
Complete the section on lexical tasks.

@@
 \newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably \emph{shifted PMI} abbreviated as \texttt{neg} and \emph{context distribution smoothing} referred to as \texttt{cds}.
-Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces, namely word vectors have almost 200000 dimensions.
-In general, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.
+Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}.
+As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.
 
-Contrary to the trend of employing highly dimensional vectors, older work on lexical distributional semantics and recent work on compositional distributional semantics employ vectors with much less dimensions, for example, 2000 \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, 3000 \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or 10000 \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
+Contrary to the trend of employing highly dimensional vectors, other work on lexical and compositional distributional semantics employ vectors with much less dimensions, for example, \textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
 
@@
 
-PMI is not directly applicable to the co-occurrence counts because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity.
+PMI is not directly applicable to the co-occurrence matrix because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity.
 A straightforward ``fix'' to this problem is to replace all infinities with zeroes.
@@
 %
-We experiment with values of 1 (absence of smoothing) and 0.75.
+We experiment with values of 1 (absence of smoothing) and 0.75 and sometimes refer to such context probability estimation as \emph{local context probability}.
 
@@
 %
-where $|C|$ is the size of the used corpus. We refer to this case as \textit{global} context probability.
+where $|C|$ is the size of the used corpus. We refer to this case as \emph{global context probability}.
 
@@
 
-As context words we select 1000, 2000, 3000, 5000, 10000, 20000, 30000, 40000 and 50000 most frequent lemmatised nouns, verbs, adjectives and adverbs.
+As context words we select 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
 All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.
@@
 
-For tasks that involve composition, we test the following operators: addition
-and multiplication \cite{mitchell2010composition}; Kronecker \cite{Grefenstette:2011:ETV:2140490.2140497}; Relational \cite{Grefenstette:2011:ESC:2145432.2145580}; Copy object and Copy subject \cite{Kartsaklis12aunified}; Frobenious addition, Frobenious multiplication and Frobenious outer \cite{kartsadrqpl2014}.
+For tasks that involve composition, we test the following operators: \textbf{addition}
+and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenious addition}, \textbf{Frobenious multiplication} and \textbf{Frobenious outer} \cite{kartsadrqpl2014}.
 
-Table~\ref{tab:parameters} list the parameters and their values used in this work.
+Table~\ref{tab:parameters} lists the parameters and their values used in this work.
 
@@
 \label{sec:lexical-experiments}
-
-\subsection{Shifted (positive) PMI performance}
 
@@
 After 10K dimensions, the average \SPMI/ performance degrades.
-\SPMI/ variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards.
+\SPMI/ score variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards.
 This suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
@@
 
-Figure~\ref{fig:simlex-ppmi-interaction} shows that 10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection.
+\input{figures/simlex-ppmi-interaction}
+
+Figure~\ref{fig:simlex-ppmi-interaction} shows dimensionality-\texttt{cds} and dimensionality-\texttt{neg} parameter interactions.
+10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection.
 For models with dimensionality greater than 10K, context distribution smoothing should be used with $\alpha = 0.75$.
 For models with dimensionality lower than 10K, it is beneficial to use global context probabilities.
-Shifting also depends on the dimensionality, models with up to 3K dimensions should set $k = 0.5$, models with up to 20k dimensions should set $k = 1.4$ and models with a higher number of dimensions should set $k = 5$.
+Shifting also depends on the dimensionality, models with up to 3K dimensions should set $k = 0.5$, models with up to 30K dimensions should set $k = 1.4$ and models with a higher number of dimensions should set $k = 2$.
 
@@
 
-\input{figures/simlex-ppmi-interaction}
+\NSPMI/ gives good results with local context probabilities ($\alpha = 1$), models with less than 20K dimensions should be used with $k = 1$, otherwise $k = 1.4$ should be preferred.
+
+We use correlation similarity metric for \SPMI/ and \NSPMI/ based models, cosine similarity is used for \logNSPMI/.
+
+The proposed heuristics work well for \logNSPMI/, where performance variance is low, the performance of models selected using the heuristics is not lower than 0.01 point of the best configuration.
+For \SPMI/ and \NSPMI/ this difference is much higher, refer to Figure~\ref{fig:simlex-ppmi-best-simlex} for more details.
+
+Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
+Again, \logNSPMI/ follows the best possible setup closely, especially for models with the dimension number greater than 10K.
+Surprisingly, the heuristics for \NSPMI/ are very effective on the MEN dataset, even though they are based on SimLex-999.
+Heuristics for \SPMI/ do not guarantee best possible results.
+
+In general, model performance depends on vector dimensionality.
+It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$).
+However, these heuristics do not guarantee the best possible result for \SPMI/ and \NSPMI/ because of high variance of the corresponding scores.
+Based on this we suggest to use \logNSPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.
 

### 2016-02-09 paper.tex
Typos

@@
 For tasks that involve composition, we test the following operators: \textbf{addition}
-and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenious addition}, \textbf{Frobenious multiplication} and \textbf{Frobenious outer} \cite{kartsadrqpl2014}.
+and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenius addition}, \textbf{Frobenius multiplication} and \textbf{Frobenius outer} \cite{kartsadrqpl2014}.
 
@@
 
-In general, model performance depends on vector dimensionality.
+In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
 It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$).
@@
 \input{figures/simlex-ppmi-best}
+
+\section{Compositional experiments}
+\label{sec:compositional-experiments}
+
+\input{figures/emnlp13-ppmi-performance}
 

### 2016-02-12 paper.tex
Compositional experiments

@@
 
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
+  \caption{\textbf{Shifted PMI mean performance and variance.}}
+  \label{fig:ppmi-performance}
+\end{figure*}
+
 \subsection{Vector dimensionality}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
-  \caption{\textbf{Shifted PMI mean performance and variance.}}
-  \label{fig:ppmi-performance}
-\end{figure*}
-
-We start with exploring the performance of SPMI, in particular \SPMI/.
 Figure~\ref{fig:ppmi-performance} shows the mean performance and the variance of the SPMI models grouped by vector dimensionality and frequency on the SimLex-999 dataset.
 
+We start with exploring the performance of \SPMI/.
 Average \SPMI/ performance increases for the dimensionality values in the range of 1K to 10K.
@@
 
+In compositional experiments, the main goal is to study compositional operators rather than special weighting schemes, therefore we will see the weighting scheme as another hyperparameter that is being optimized and study compositional operators in isolation.
+
+Figure~\ref{fig:emnlp13-ppmi-performance} shows SPMI's average performance and evaluation score variance on the KS14 dataset.
+
+Addition has the highest average performance and a relatively low variance.
+Multiplication, shows lowest average performance, but the result variance is much higher than addition.
+Kronecker exhibits behavior similar to multiplication.
+
+\subsection{Addition}
+\label{sec:addition}
+
 %\bibliographystyle{acl}

### 2016-02-12 paper.tex
Intro

@@
 \label{sec:introduction}
+
+Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text.
+If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
+\newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
+\emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
+Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word.
+A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association.
+This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.
+
+Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics.
+The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
+These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.
 

### 2016-02-16 figures/performance-mean-var.tex
Lexical tasks

\begin{figure*}
  \centering
  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-performance-mean}
  \caption{Mean.}
  \label{fig:performance-mean}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-performance-var}
  \caption{Variance.}
  \label{fig:performance-var}
  \end{subfigure}

  \caption{\textbf{Mean performance and variance.}}
  \label{fig:performance-mean-var}

\end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2016-02-16 paper.tex
Grammar
Lexical tasks

@@
 \makeatother
-\usepackage{hyperref}
+% \usepackage{hyperref}
 
@@
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence performance of highly dimensional models the same way as lowly dimensional models? Are finding of \newcite{TACL570} directly transferred to lowly dimensional models?
+\item Do parameters influence performance of highly dimensional models the same way as lowly dimensional models? Can the findings of \newcite{TACL570} be directly applied to lowly dimensional models?
 \item Is it possible to come up with the heuristics for model parameter selection? If so, what are they?
-\item Can the heuristics based on lexical tasks be transferred to compositional tasks?
 \end{itemize}
 
-To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}; and three compositional datasets: KS14 \cite{kartsadrqpl2014}, GS11 \cite{Grefenstette:2011:ESC:2145432.2145580} and PhraseRel.
+To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}.
+
+\input{figures/parameters}
 
@@
 \label{sec:parameters}
-
-\input{figures/parameters}
 
@@
 
+\input{figures/performance-mean-var}
+
 \subsection{Frequency weighting (\texttt{freq})}
@@
 
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi}
-  \caption{\textbf{Shifted PMI mean performance and variance.}}
-  \label{fig:ppmi-performance}
-\end{figure*}
-
 \subsection{Vector dimensionality}
@@
 
-\subsection{Compositional operator}
-\label{sec:comp-oper}
-
-For tasks that involve composition, we test the following operators: \textbf{addition}
-and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenius addition}, \textbf{Frobenius multiplication} and \textbf{Frobenius outer} \cite{kartsadrqpl2014}.
-
 Table~\ref{tab:parameters} lists the parameters and their values used in this work.
 
-\section{Lexical experiments}
+\section{Experiments}
 \label{sec:lexical-experiments}
 
-Figure~\ref{fig:ppmi-performance} shows the mean performance and the variance of the SPMI models grouped by vector dimensionality and frequency on the SimLex-999 dataset.
+Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.
 
-We start with exploring the performance of \SPMI/.
-Average \SPMI/ performance increases for the dimensionality values in the range of 1K to 10K.
-After 10K dimensions, the average \SPMI/ performance degrades.
-\SPMI/ score variance is the smallest for the 10K dimensional models and it grows as the dimension number increases afterwards.
-This suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
+PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.
 
-Interestingly, \logNSPMI/ mean performance increases and variance decreases as dimensionality increases showing that this weighting is not sensitive to the parameter selection for highly dimensional models.
+CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.
 
-\paragraph{Parameter interaction}
+Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.
 
-\input{figures/simlex-ppmi-interaction}
+Finally, SCPMI behaves very similarly to SPMI but with higher variance.
 
-Figure~\ref{fig:simlex-ppmi-interaction} shows dimensionality-\texttt{cds} and dimensionality-\texttt{neg} parameter interactions.
+High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
+
+\subsection{Parameter interaction and heuristic derivation}
+
+\input{figures/interaction-cds}
+
+Figures~\ref{fig:interaction-cds}~and~~\ref{fig:interaction-neg} show dimensionality-\texttt{cds} and dimensionality-\texttt{neg} parameter interactions.
+
+\paragraph{PMI and CPMI}
+
+PMI achieves the highest performance with global context probabilities.
+CPMI should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
+
+\paragraph{SPMI}
+
 10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection.
-For models with dimensionality greater than 10K, context distribution smoothing should be used with $\alpha = 0.75$.
-For models with dimensionality lower than 10K, it is beneficial to use global context probabilities.
-Shifting also depends on the dimensionality, models with up to 3K dimensions should set $k = 0.5$, models with up to 30K dimensions should set $k = 1.4$ and models with a higher number of dimensions should set $k = 2$.
+For models with dimensionality greater than 20K, context distribution smoothing should be used with $\alpha = 0.75$.
+For models with dimensionality lower than 20K, it is beneficial to use global context probabilities.
+Shifting also depends on the dimensionality, models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$.
+Note, however, that there might be a finer grained $k$ tuning which we avoid in order to avoid overfitting.
 
-\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 10K.
-For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$.
-Shifting should be applied with $\alpha = 0.5$ for models with less than 10K dimensions and $\alpha = 1.4$ for models with more than 10K dimensions.
+\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 20K.
+For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$, which is similar to \SPMI/.
+Shifting should be applied with $\alpha = 1.4$ for models with less than 20K dimensions and $\alpha = 5$ for models with more than 20K dimensions.
+In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $\alpha = 1.4$ is a much robust choice for \logNSPMI/.
 
-\NSPMI/ gives good results with local context probabilities ($\alpha = 1$), models with less than 20K dimensions should be used with $k = 1$, otherwise $k = 1.4$ should be preferred.
+\NSPMI/ gives good results with local context probabilities ($\alpha = 1$). Models with less than 20K dimensions should be used with $k = 1.4$, otherwise $k = 5$ should be preferred.
 
-We use correlation similarity metric for \SPMI/ and \NSPMI/ based models, cosine similarity is used for \logNSPMI/.
+\paragraph{SCPMI}
+
+With \SCPMI/ and vectors with dimensionality less than 20K global context probability should be used and shifting should be set to $k = 0.7$.
+Otherwise, local context probability should be used with $\alpha = 0.75$ and $k = 2$.
+
+\NSCPMI/ with dimensions less than 20K global context probability should be used and $k = 1.4$. Otherwise local context probability without smoothing and $k = 5$ is suggested.
+
+\logNSCPMI/ with models with less than 20K dimensions gives the highest average results with global context probabilities and $k = 0.7$.
+Otherwise, local context probabilities without smoothing should be preferred with $k = 1.4$.
+
+% We use correlation similarity metric for \SPMI/ and \NSPMI/ based models, cosine similarity is used for \logNSPMI/.
+
+\subsection{Heurisitc evaluation}
+\label{sec:heurisitc-evaluation}
+
+We evaluate the models selected using the heuristics described above against the best possible selection for a given dimensionality choice on the SimLex-999 dataset (refer to Figure~\ref{fig:simlex-ppmi-best-simlex}).
+
+Heuristics for \logNPMI/ and \logNCPMI/ pick the best possible models.
 
 The proposed heuristics work well for \logNSPMI/, where performance variance is low, the performance of models selected using the heuristics is not lower than 0.01 point of the best configuration.
-For \SPMI/ and \NSPMI/ this difference is much higher, refer to Figure~\ref{fig:simlex-ppmi-best-simlex} for more details.
+For \SPMI/ and \NSPMI/ this difference is much higher.
+
+Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the PPMI models. In general $n$ weighted models do not perform as good as others.
 
 Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
-Again, \logNSPMI/ follows the best possible setup closely, especially for models with the dimension number greater than 10K.
-Surprisingly, the heuristics for \NSPMI/ are very effective on the MEN dataset, even though they are based on SimLex-999.
-Heuristics for \SPMI/ do not guarantee best possible results.
+Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection.
 
@@
 It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$).
-However, these heuristics do not guarantee the best possible result for \SPMI/ and \NSPMI/ because of high variance of the corresponding scores.
-Based on this we suggest to use \logNSPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.
+However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of high variance of the corresponding scores.
+Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.
 
-\input{figures/simlex-ppmi-best}
+\input{figures/interaction-neg}
 
-\section{Compositional experiments}
-\label{sec:compositional-experiments}
-
-\input{figures/emnlp13-ppmi-performance}
-
-In compositional experiments, the main goal is to study compositional operators rather than special weighting schemes, therefore we will see the weighting scheme as another hyperparameter that is being optimized and study compositional operators in isolation.
-
-Figure~\ref{fig:emnlp13-ppmi-performance} shows SPMI's average performance and evaluation score variance on the KS14 dataset.
-
-Addition has the highest average performance and a relatively low variance.
-Multiplication, shows lowest average performance, but the result variance is much higher than addition.
-Kronecker exhibits behavior similar to multiplication.
-
-\subsection{Addition}
-\label{sec:addition}
+\input{figures/best}
 
@@
 % remove publisher, month etc from conf proceedings:
-\bibliographystyle{acl-short}
-% \bibliographystyle{naaclhlt2016}
+% \bibliographystyle{acl-short}
+\bibliographystyle{acl2016}
 \balance

### 2016-02-16 paper.tex
Shortening the paper.

@@
 
-Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text.
+% Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text.
 If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
-\newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
-\emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
-Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word.
+% \newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
+% \emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
+% Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word.
 A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association.
@@
 
-Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics.
+% Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics.
 The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
-These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.
+% These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.
 
@@
 To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}.
-
-\input{figures/parameters}
 
@@
 
-Table~\ref{tab:parameters} lists the parameters and their values used in this work.
-
 \section{Experiments}
@@
 
-Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.
+\input{figures/parameters}
 
-PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.
+Table~\ref{tab:parameters} lists parameters used in this work, their values and the proportion of score variance explained by the parameter and it's two-way interaction corresponding to the reduction in adjusted $R^2$ (0.61 if all parameters and their combinations are taken into account) if this parameter is left out using the analysis of variance, where the model score is a dependant variable and the model parameters are independent variables, refer to \newcite{lapesa2014large} for more details.
 
-CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.
+% ----------
 
-Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.
+% Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.
 
-Finally, SCPMI behaves very similarly to SPMI but with higher variance.
+% PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.
 
-High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
+% CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.
 
-\subsection{Parameter interaction and heuristic derivation}
+% Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.
+
+% Finally, SCPMI behaves very similarly to SPMI but with higher variance.
+
+% High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
+
+\subsection{Heuristic derivation}
 

### 2016-02-17 paper.tex
Clean up.

@@
 
+\input{figures/interaction-cds}
+
 \subsection{PMI variants (\texttt{discr})}
@@
 
+\input{figures/parameters}
+
 \subsection{Shifted PMI (\texttt{neg})}
@@
 %
-As $k$ increases, more values become 0 and, consequently, vectors become sparser. Setting $k$ to 1 is equivalent to vanilla positive PMI without shifting. When $k < 1$ vectors are denser.
-
-Finally, we can apply the same idea to CPMI:
+We can apply the same idea to CPMI:
 %
@@
 \end{equation}
-
-\input{figures/performance-mean-var}
 
@@
 In addition to $1$ and $n$ frequencies, we experiment with $\log n$ frequency.
+
+\input{figures/interaction-neg}
 
@@
 
-\input{figures/parameters}
-
-Table~\ref{tab:parameters} lists parameters used in this work, their values and the proportion of score variance explained by the parameter and it's two-way interaction corresponding to the reduction in adjusted $R^2$ (0.61 if all parameters and their combinations are taken into account) if this parameter is left out using the analysis of variance, where the model score is a dependant variable and the model parameters are independent variables, refer to \newcite{lapesa2014large} for more details.
-
-% ----------
-
-% Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.
-
-% PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.
-
-% CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.
-
-% Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.
-
-% Finally, SCPMI behaves very similarly to SPMI but with higher variance.
-
-% High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.
-
-\subsection{Heuristic derivation}
-
-\input{figures/interaction-cds}
-
-Figures~\ref{fig:interaction-cds}~and~~\ref{fig:interaction-neg} show dimensionality-\texttt{cds} and dimensionality-\texttt{neg} parameter interactions.
+Table~\ref{tab:parameters} lists parameters used in this work and their values.
+We will derive the parameter selection heuristics by greedily selecting parameters (\texttt{cds}, \texttt{neg} and similarity measure) that lead to the highest average performance for each frequency, discriminativeness and context combination.
+Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show such interaction of \texttt{cds} and \texttt{neg} with other parameters, we don not report similarity behavior due to the limited space.
 
@@
 
-% We use correlation similarity metric for \SPMI/ and \NSPMI/ based models, cosine similarity is used for \logNSPMI/.
-
 \subsection{Heurisitc evaluation}
 \label{sec:heurisitc-evaluation}
+
+\input{figures/best}
 
@@
 
+\section{Conclusion}
+\label{sec:conclusion}
+
+This paper presents a systematic study of co-occurrence quantification focusing of the selection of parameters presented in \newcite{TACL570}.
+We replicate their recommendation for highly dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with lowly dimensional spaces.
+As an outcome of such an analysis we propose a set of model selection heuristics that maximize performance.
+
 In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$).
-However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of high variance of the corresponding scores.
+It is beneficial to experiment with dense and unsmoothed lowly dimensional spaces ($k < 1$, global context probability); and sparse and smooth highly dimensional spaces ($k > 1$, $\alpha = 0.75$).
+However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.
 Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.
-
-\input{figures/interaction-neg}
-
-\input{figures/best}
 

### 2016-02-19 figures/best.tex
Lexical tasks
Figures

--- 2016-02-07 figures/simlex-ppmi-best.tex
@@
   \centering
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-best.pdf}
+  \begin{subfigure}[b]{\textwidth}
+    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/SimLex999-best}}
+    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393.
+      This work: 0.385,
+      SGNS: 0.438,
+      GloVe: 0.398.
+    }
+    \label{fig:simlex-ppmi-best-simlex}
+  \end{subfigure}
 
-  \caption{\textbf{SPMI best configurations.}}
+  \begin{subfigure}[b]{\textwidth}
+    \centerline{\includegraphics[width=1.1\textwidth]{supplement/figures/men-best}}
+    \caption{\textbf{MEN.} The black line refers to the score of 0.745.
+      This work: 0.765,
+      SGNS: 0.774,
+      GloVe: 0.729.
+    }
+    \label{fig:simlex-ppmi-best-men}
+  \end{subfigure}
+
+  \caption{\textbf{SPMI best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}.
+We also give our best score, SGNS and GloVe numbers from that study for comparison.}
   \label{fig:simlex-ppmi-best}

### 2016-02-19 paper.tex
Figures

@@
 
-\def\relevant/{Relevant@3}
-\def\topRR/{Top Reciprocal Rank}
-\def\RR/{Reciprocal Rank}
-
 \begin{document}
@@
 
-% Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text.
-If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
-% \newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
-% \emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
-% Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word.
-A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association.
-This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.
-
-% Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics.
-The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
-% These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.
-
-\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably \emph{shifted PMI} abbreviated as \texttt{neg} and \emph{context distribution smoothing} referred to as \texttt{cds}.
+\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably shifting and context distribution smoothing.
 Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}.
@@
 A straightforward ``fix'' to this problem is to replace all infinities with zeroes.
-Such a replacement preserve sparsity of the input co-occurrence matrix.
 Later in the paper, we use PMI to refer to a weighting with this fix.
@@
 
-10K dimensional \SPMI/ is, indeed, the least sensitive to parameter selection.
+10K dimensional \SPMI/ is the least sensitive to parameter selection.
 For models with dimensionality greater than 20K, context distribution smoothing should be used with $\alpha = 0.75$.
@@
 Shifting also depends on the dimensionality, models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$.
-Note, however, that there might be a finer grained $k$ tuning which we avoid in order to avoid overfitting.
+Note, however, that there might be a finer grained $k$ selection criteria, which we do not report in order to avoid overfitting.
 
@@
 For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$, which is similar to \SPMI/.
-Shifting should be applied with $\alpha = 1.4$ for models with less than 20K dimensions and $\alpha = 5$ for models with more than 20K dimensions.
-In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $\alpha = 1.4$ is a much robust choice for \logNSPMI/.
+Shifting should be applied with $k = 0.5$ for models with less than 20K dimensions and $k = 1.4$ for models with more than 20K dimensions.
+In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $k = 1.4$ is a much robust choice for \logNSPMI/.
 
@@
 
-\NSCPMI/ with dimensions less than 20K global context probability should be used and $k = 1.4$. Otherwise local context probability without smoothing and $k = 5$ is suggested.
+\NSCPMI/ with dimensions less than 20K should using with global context probability and $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.
 
@@
 
-Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the PPMI models. In general $n$ weighted models do not perform as good as others.
+Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as good as others.
 
 Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
-Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection.
+Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.
 

### 2016-02-22 paper.tex
Abstract

@@
 
-\title{\ldots}
+\title{Robust co-occurrence quantification for lexical distributional semantics experiments}
 
@@
 
-\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably shifting and context distribution smoothing.
+\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, namely shifting and context distribution smoothing.
 Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}.
-As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.
+As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
 
@@
 
+\input{figures/best}
+
 \logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 20K.
@@
 \label{sec:heurisitc-evaluation}
-
-\input{figures/best}
 

### 2016-02-25 paper.tex
Submission id.
lowly -> low

@@
-\documentclass[11pt,letterpaper]{article}
+\documentclass[11pt]{article}
 \usepackage{acl2016}
@@
 \sloppy
+
+% \aclfinalcopy % Uncomment this line for the final submission
+\def\aclpaperid{34} %  Enter the acl Paper ID here
 
@@
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence performance of highly dimensional models the same way as lowly dimensional models? Can the findings of \newcite{TACL570} be directly applied to lowly dimensional models?
+\item Do parameters influence performance of highly dimensional models the same way as low dimensional models? Can the findings of \newcite{TACL570} be directly applied to low dimensional models?
 \item Is it possible to come up with the heuristics for model parameter selection? If so, what are they?
@@
 This paper presents a systematic study of co-occurrence quantification focusing of the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for highly dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with lowly dimensional spaces.
+We replicate their recommendation for highly dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low dimensional spaces.
 As an outcome of such an analysis we propose a set of model selection heuristics that maximize performance.
@@
 In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-It is beneficial to experiment with dense and unsmoothed lowly dimensional spaces ($k < 1$, global context probability); and sparse and smooth highly dimensional spaces ($k > 1$, $\alpha = 0.75$).
+It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth highly dimensional spaces ($k > 1$, $\alpha = 0.75$).
 However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.

### 2016-02-25 paper.tex
MP edits

@@
 
-\title{Robust co-occurrence quantification for lexical distributional semantics experiments}
+%\title{Robust co-occurrence quantification for lexical distributional semantics experiments}
+% MP: how about:
+\title{Robust co-occurrence quantification for low-dimensional lexical distributional semantics}
 
@@
 
-\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, namely shifting and context distribution smoothing.
-Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}.
-As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
+\newcite{TACL570} propose optimisations for co-occrrence-based distributional models, using parameters adopted from predictive models \cite{mikolov2013efficient}: \emph{shifting} and \emph{context distribution smoothing}.
+Their experiments and thus their parameter  recommendations use high-dimensional vector spaces with word vector dimensionality of almost \textbf{200K}, and many recent state-of-the-art results in lexical distributional semantics have been obtained using vectors with similar dimensionality  \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
 
-Contrary to the trend of employing highly dimensional vectors, other work on lexical and compositional distributional semantics employ vectors with much less dimensions, for example, \textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
+In contrast, much work on \emph{compositional} distributional semantics employs vectors with much fewer dimensions: e.g.~\textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
+\textbf{MP: say why}
 
-Such a mismatch in vector dimensionality selection across lexical and compositional tasks rises a number of questions this paper aims to answer.
+Such a mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
 \begin{itemize}
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence performance of highly dimensional models the same way as low dimensional models? Can the findings of \newcite{TACL570} be directly applied to low dimensional models?
-\item Is it possible to come up with the heuristics for model parameter selection? If so, what are they?
+\item Do parameters influence performance of high-dimensional and low-dimensional models in the same way? Can the findings of \newcite{TACL570} be directly applied to low-dimensional models?
+\item If not, can we derive suitable parameter selection heuristics which take account of dimensionality?
 \end{itemize}
 
-To answer these questions we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}.
+To answer these, we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}.
 
@@
 
-Co-occurrence weightings schemes based on \emph{Point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) have been successfully applied in distributional semantics (see for example \newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756} and \newcite{NIPS2014_5477}).
+Co-occurrence weighting schemes based on \emph{Point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) have been successfully applied in distributional semantics (see e.g.~\newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756}, \newcite{NIPS2014_5477}).
 %
@@
 
-It has been experimentally shown that negative PMI values do not positively contribute to model performance and worth nullifying \cite{Turney:2010:FMV:1861751.1861756}.
-Positive PMI extended with an additional additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570} is the third PMI variant (abbreviated as SPMI) used in this work:
+Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance \cite{Turney:2010:FMV:1861751.1861756}.
+This can be generalised as an additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
 %
@@
 
-We test a widely used cosine based similarity, as well as correlation \cite{kiela-clark:2014:CVSC}.
+We test a widely used cosine based similarity, as well as correlation \cite{kiela-clark:2014:CVSC}. \textbf{MP: I would move this to next section: it's not really a parameter here}
 
@@
 
-\subsection{Heurisitc evaluation}
-\label{sec:heurisitc-evaluation}
+\subsection{Evaluation of heuristics}
+\label{sec:heuristic-evaluation}
 
@@
 This paper presents a systematic study of co-occurrence quantification focusing of the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for highly dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low dimensional spaces.
+We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low-dimensional spaces.
 As an outcome of such an analysis we propose a set of model selection heuristics that maximize performance.
@@
 In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth highly dimensional spaces ($k > 1$, $\alpha = 0.75$).
+It is beneficial to experiment with dense and unsmoothed low-dimensional spaces ($k < 1$, global context probability); and sparse and smooth high-dimensional spaces ($k > 1$, $\alpha = 0.75$).
 However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.

### 2016-02-27 figures/interaction-cds.tex
Lexical tasks
Figures
Update

--- 2016-02-07 figures/simlex-ppmi-interaction.tex
@@
   \centering
-  \begin{subfigure}[b]{\textwidth}
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-cds.pdf}
-    \caption{\textbf{Context distribution smoothing.}}
-    \label{fig:simlex-ppmi-interaction-cds}
-  \end{subfigure}
-
-  \begin{subfigure}[b]{\textwidth}
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-neg.pdf}
-    \caption{\textbf{Shifting.}}
-    \label{fig:simlex-ppmi-interaction-neg}
-  \end{subfigure}
-
-  \caption{\textbf{SPMI.}}
-  \label{fig:simlex-ppmi-interaction}
+    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-cds}}
+    \caption{\textbf{The effect of context probability estimation and smoothing on SimLex-999.}}
+    \label{fig:interaction-cds}
 \end{figure*}

### 2016-02-27 figures/interaction-neg.tex
Lexical tasks
Figures
Update

--- 2016-02-07 figures/simlex-ppmi-interaction.tex
@@
   \centering
-  \begin{subfigure}[b]{\textwidth}
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-cds.pdf}
-    \caption{\textbf{Context distribution smoothing.}}
-    \label{fig:simlex-ppmi-interaction-cds}
-  \end{subfigure}
-
-  \begin{subfigure}[b]{\textwidth}
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-neg.pdf}
-    \caption{\textbf{Shifting.}}
-    \label{fig:simlex-ppmi-interaction-neg}
-  \end{subfigure}
-
-  \caption{\textbf{SPMI.}}
-  \label{fig:simlex-ppmi-interaction}
+    \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-neg}}
+    \caption{\textbf{The behaviour of shifted PMI on SimLex-999.}}
+    \label{fig:interaction-neg}
 \end{figure*}

### 2016-02-27 paper.tex
Update

@@
 
-%\title{Robust co-occurrence quantification for lexical distributional semantics experiments}
-% MP: how about:
 \title{Robust co-occurrence quantification for low-dimensional lexical distributional semantics}
@@
 In contrast, much work on \emph{compositional} distributional semantics employs vectors with much fewer dimensions: e.g.~\textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
-\textbf{MP: say why}
+These models  assign tensors to functional words: intransitive verbs and adjectives have  tensors of rank 2,  transitive verbs  rank 3, prepositions rank 7.
+Tensors are highly dimensional objects, for $V$ a vector space with dimension $k$,  a tensor $V \otimes V \cdots \otimes V$ of rank $n$ over it has dimension  $n^k$.
+In these models, if one takes $n= \textbf{30k}$, then one will end up with   spaces with intractable dimensions  $\textbf{30k}^2, \textbf{30k}^3$ and $\textbf{30k}^7$.
 
 Such a mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
-\begin{itemize}
+\begin{compactitem}
 \item To what extent does model performance depend on vector dimensionality?
@@
 \item If not, can we derive suitable parameter selection heuristics which take account of dimensionality?
-\end{itemize}
+\end{compactitem}
 
@@
 
-An alternative solution of avoiding infinity is to increment the probability ratio by one:
+An alternative solution of avoiding infinity is to increment the probability ratio by one, we refer to it as \textit{compressed} PMI:
 %
@@
 Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance \cite{Turney:2010:FMV:1861751.1861756}.
-This can be generalised as an additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
+This can be generalised as an additional parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
 %
@@
 
-\subsection{Similarity metric}
-\label{sec:similarity-metric}
-
-We test a widely used cosine based similarity, as well as correlation \cite{kiela-clark:2014:CVSC}. \textbf{MP: I would move this to next section: it's not really a parameter here}
-
 \section{Experiments}
@@
 Table~\ref{tab:parameters} lists parameters used in this work and their values.
-We will derive the parameter selection heuristics by greedily selecting parameters (\texttt{cds}, \texttt{neg} and similarity measure) that lead to the highest average performance for each frequency, discriminativeness and context combination.
-Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show such interaction of \texttt{cds} and \texttt{neg} with other parameters, we don not report similarity behavior due to the limited space.
+We will derive the parameter selection heuristics by greedily selecting parameters (\texttt{cds} and \texttt{neg}) that lead to the highest average performance for each frequency, discriminativeness and context combination.
+Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show such interaction of \texttt{cds} and \texttt{neg} with other parameters.
+We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report their behaviour in details due to the limited space.
 
@@
 
-\subsection{Evaluation of heuristics}
+\paragraph{Evaluation of heuristics}
 \label{sec:heuristic-evaluation}

### 2016-02-29 paper.tex
SharedLatex

--- 2016-02-25 paper.tex
@@
 \newcite{TACL570} propose optimisations for co-occrrence-based distributional models, using parameters adopted from predictive models \cite{mikolov2013efficient}: \emph{shifting} and \emph{context distribution smoothing}.
-Their experiments and thus their parameter  recommendations use high-dimensional vector spaces with word vector dimensionality of almost \textbf{200K}, and many recent state-of-the-art results in lexical distributional semantics have been obtained using vectors with similar dimensionality  \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
+Their experiments and thus their parameter  recommendations use high-dimensional vector spaces with word vector dimensionality of almost \textbf{200K}, and many recent state-of-the-art results in lexical distributional semantics have been obtained using vectors with similarly high dimensionality  \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
 
 In contrast, much work on \emph{compositional} distributional semantics employs vectors with much fewer dimensions: e.g.~\textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
-\textbf{MP: say why}
+These models  assign tensors to functional words; for a vector space $V$ with dimension $k$,  a tensor $V \otimes V \cdots \otimes V$ of rank $n$ has dimension  $n^k$.
+As intransitive verbs and adjectives have  tensors of rank 2,  transitive verbs  rank 3, and prepositions rank 7,
+if one takes $n= \textbf{30k}$ one will end up with   spaces with intractable dimensions  $\textbf{30}^\textbf{2} \textbf{k}$, $\textbf{30}^\textbf{3} \textbf{k}$ and $\textbf{30}^\textbf{7} \textbf{k}$.
 
-Such a mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
-\begin{itemize}
+This mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
+\begin{compactitem}
 \item To what extent does model performance depend on vector dimensionality?
@@
 
-Co-occurrence weighting schemes based on \emph{Point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) have been successfully applied in distributional semantics (see e.g.~\newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756}, \newcite{NIPS2014_5477}).
+Most co-occurrence weighting schemes in distributional semantics are based on \emph{point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) (see e.g.~\newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756}, \newcite{NIPS2014_5477}).
 %
@@
 
-PMI is not directly applicable to the co-occurrence matrix because non-observed co-occurrences lead to infinite PMI values which in turn make it impossible to compute similarity.
-A straightforward ``fix'' to this problem is to replace all infinities with zeroes.
-Later in the paper, we use PMI to refer to a weighting with this fix.
+PMI in its raw form is problematic: non-observed co-occurrences lead to infinite PMI values, making it impossible to compute similarity.
+A common ``fix'' to this problem is to replace all infinities with zeroes, and we use PMI hereafter to refer to a weighting with this fix.
 
-An alternative solution of avoiding infinity is to increment the probability ratio by one:
+An alternative solution is to increment the probability ratio by 1; we refer to this as \textit{compressed PMI} (CPMI):
 %
@@
 Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance \cite{Turney:2010:FMV:1861751.1861756}.
-This can be generalised as an additional hyperparameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
+This can be generalised as an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
 %
@@
 
-Another issue with PMI is its bias towards rare events \cite{TACL570} one way of solving this issue is to weight PMI value by the co-occurrence frequency \cite{Evert05}:
+Another issue with PMI is its bias towards rare events \cite{TACL570}; one way of solving this issue is to weight the value by the co-occurrence frequency \cite{Evert05}:
 %
@@
 where $n(x, y)$ is the number of times $x$ was seen together with $y$.
-For clarity, we refer to $n$ weighted PMIs as \NPMI/, \NSPMI/ \NCPMI/ and \NSCPMI/.
-When frequency component is set to 1, it does not have an effect giving rise to explicit quantification labels: \PMI/, \SPMI/, \CPMI/ and \SCPMI/.
+For clarity, we refer to $n$-weighted PMIs as \NPMI/, \NSPMI/, \NCPMI/ and \NSCPMI/.
+When this weighting component is set to 1, it has no effect; we can  explicitly label this \PMI/, \SPMI/, \CPMI/ and \SCPMI/.
 
-In addition to $1$ and $n$ frequencies, we experiment with $\log n$ frequency.
+In addition to $1$ and $n$ weightings, we experiment with a $\log n$ weighting.
+% \textbf{MP: cite ref for this?}
 
@@
 
-Context distribution smoothing (\texttt{cds}) is another parameter shown to influence performance of distributional models \cite{TACL570}. It smoothes the context distribution $P(x)$:
+\newcite{TACL570} show that performance is affected by smoothing the context distribution $P(x)$:
 %
@@
 %
-We experiment with values of 1 (absence of smoothing) and 0.75 and sometimes refer to such context probability estimation as \emph{local context probability}.
-
-We also estimate probability of a context using the global context appearance in the corpus:
+We experiment with $\alpha$ values of 1 (no smoothing) and 0.75.
+We refer to this estimation method as \emph{local context probability}; we can also estimate a \emph{global context probability} based on global context appearance:
 %
@@
 %
-where $|C|$ is the size of the used corpus. We refer to this case as \emph{global context probability}.
+where $|C|$ is the size of the used corpus.
 
@@
 
-As context words we select 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
-All context words are part of speech tagged, but we do not make difference between refined word types, for example, we do not distinguish between transitive and ditransitive verbs.
-
-\subsection{Similarity metric}
-\label{sec:similarity-metric}
-
-We test a widely used cosine based similarity, as well as correlation \cite{kiela-clark:2014:CVSC}. \textbf{MP: I would move this to next section: it's not really a parameter here}
+As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
+All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.
+transitive vs.
+ditransitive versions of verbs).
 
@@
 Table~\ref{tab:parameters} lists parameters used in this work and their values.
-We will derive the parameter selection heuristics by greedily selecting parameters (\texttt{cds}, \texttt{neg} and similarity measure) that lead to the highest average performance for each frequency, discriminativeness and context combination.
-Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show such interaction of \texttt{cds} and \texttt{neg} with other parameters, we don not report similarity behavior due to the limited space.
+As the source corpus we use the concatenation of Wackypedia and ukWaC \cite{Baroni2009} using a symmetric window of 5 words (following \newcite{milajevs-EtAl:2014:EMNLP2014}); our evaluation metric is the correlation with human judgements as standardly used with SimLex \cite{hill2014simlex}.
+We derive our parameter selection heuristics by greedily selecting parameters (\texttt{cds} and \texttt{neg}) that lead to the highest average performance for each combination of frequency weighting, PMI variant and dimensionality.
+Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show the interaction of \texttt{cds} and \texttt{neg} with other parameters.
+We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report detailed results due to limited space.
 
@@
 
-PMI achieves the highest performance with global context probabilities.
-CPMI should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
+PMI should be used with global context probabilities.
+\NCPMI/ and \logNCPMI/ should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
 
@@
 For models with dimensionality lower than 20K, it is beneficial to use global context probabilities.
-Shifting also depends on the dimensionality, models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$.
+Shifting also depends on the dimensionality: models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$.
 Note, however, that there might be a finer grained $k$ selection criteria, which we do not report in order to avoid overfitting.
@@
 
-With \SCPMI/ and vectors with dimensionality less than 20K global context probability should be used and shifting should be set to $k = 0.7$.
+With \SCPMI/ and vector dimensionality less than 20K, global context probability should be used and shifting should be set to $k = 0.7$.
 Otherwise, local context probability should be used with $\alpha = 0.75$ and $k = 2$.
 
-\NSCPMI/ with dimensions less than 20K should using with global context probability and $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.
+With \NSCPMI/ and dimensions less than 20K, global context probability should be used with $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.
 
-\logNSCPMI/ with models with less than 20K dimensions gives the highest average results with global context probabilities and $k = 0.7$.
-Otherwise, local context probabilities without smoothing should be preferred with $k = 1.4$.
+For \logNSCPMI/, models with less than 20K dimensions should be used with global context probabilities and $k = 0.7$; otherwise, local context probabilities without smoothing should be preferred with $k = 1.4$.
 
-\subsection{Evaluation of heuristics}
+\paragraph{Evaluation of heuristics}
 \label{sec:heuristic-evaluation}
 
-We evaluate the models selected using the heuristics described above against the best possible selection for a given dimensionality choice on the SimLex-999 dataset (refer to Figure~\ref{fig:simlex-ppmi-best-simlex}).
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:simlex-ppmi-best-simlex}).
 
-Heuristics for \logNPMI/ and \logNCPMI/ pick the best possible models.
-
-The proposed heuristics work well for \logNSPMI/, where performance variance is low, the performance of models selected using the heuristics is not lower than 0.01 point of the best configuration.
+For \logNPMI/ and \logNCPMI/, our heuristics pick the best possible models.
+For \logNSPMI/, where performance variance is low, the heuristics do well, giving performance no more than 0.01 points below the best configuration.
 For \SPMI/ and \NSPMI/ this difference is much higher.
 
-Heuristics for \logNCPMI/ and \CPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as good as others.
+Heuristics for \logNSCPMI/and \SCPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as well as others.
 
-Finally, to see whether the heuristics are applicable to other datasets, we contrast the selected models with the best scores on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
+$\log n$ weighting should be used with PMI, CPMI and SCPMI.
+High-dimensional SPMI models show the same behaviour, but if vector dimensionality is less than 10K, no weighting should be applied.
+SPMI and SCPMI should be preferred over CPMI and PMI.
+
+Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
 Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.
+
+% \textbf{MP: is it worth including a line for the *worst* possible parameter selection too?
+Or for the average; or for the Levy/Goldberg "standard" parameters?
+That way the reader can see how much benefit the heuristics give.
+}
 
@@
 In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-It is beneficial to experiment with dense and unsmoothed low-dimensional spaces ($k < 1$, global context probability); and sparse and smooth high-dimensional spaces ($k > 1$, $\alpha = 0.75$).
+Low-dimensional spaces benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
 However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.

### 2016-02-29 figures/global-best.tex
Global best

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centerline{\includegraphics[width=\textwidth]{supplement/figures/SimLex999-global-best}}
    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393.
      This work: 0.385,
      SGNS: 0.438,
      GloVe: 0.398.
    }
    \label{fig:global-best-simlex}
  \end{subfigure}
~
  \begin{subfigure}[b]{0.49\textwidth}
    \centerline{\includegraphics[width=\textwidth]{supplement/figures/men-global-best}}
    \caption{\textbf{MEN.} The black line refers to the score of 0.745.
      This work: 0.765,
      SGNS: 0.774,
      GloVe: 0.729.
    }
    \label{fig:global-best-men}
  \end{subfigure}

  \caption{\textbf{Best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}. We also give our best, average, worst scores and models that are selected with the recommendations from \protect\newcite{TACL570}.
SGNS and GloVe numbers are reported from \protect\newcite{TACL570} for comparison.}
  \label{fig:global-best}
\end{figure*}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

### 2016-02-29 paper.tex
Global best

@@
 
-\input{figures/best}
+\input{figures/global-best}
 
@@
 
-We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:simlex-ppmi-best-simlex}).
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:global-best-simlex}).
 
@@
 
-Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
+Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:global-best-men}).
 Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.

### 2016-02-29 figures/best.tex
Figure merge

--- 2016-02-07 figures/simlex-ppmi-best.tex
@@
   \centering
-    \includegraphics[width=\textwidth]{supplement/figures/simlex-ppmi-best.pdf}
+  \begin{subfigure}[t]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-best}
+    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393. \\
+      This work: 0.385,
+      SGNS: 0.438,
+      GloVe: 0.398.
+    }
+    \label{fig:best-simlex}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.37\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/SimLex999-global-best}
+    \caption{\textbf{SimLex-999.}
+    }
+    \label{fig:global-best-simlex}
+  \end{subfigure}
 
-  \caption{\textbf{SPMI best configurations.}}
-  \label{fig:simlex-ppmi-best}
+  \begin{subfigure}[t]{0.6\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/men-best}
+    \caption{\textbf{MEN.} The black line refers to the score of 0.745. \\
+      This work: 0.765,
+      SGNS: 0.774,
+      GloVe: 0.729.
+    }
+    \label{fig:best-men}
+  \end{subfigure}
+  ~
+  \begin{subfigure}[t]{0.37\textwidth}
+    \includegraphics[width=\textwidth]{supplement/figures/men-global-best}
+    \caption{\textbf{MEN.}
+    }
+    \label{fig:global-best-men}
+  \end{subfigure}
+
+  \caption{\textbf{Best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}.
+We also give our best score, SGNS and GloVe numbers from that study for comparison.}
+  \label{fig:best}
 \end{figure*}

### 2016-02-29 paper.tex
Figure merge

--- 2016-02-29 paper.tex
@@
 
-We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:simlex-ppmi-best-simlex}).
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:best-simlex}).
 
@@
 
-Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:simlex-ppmi-best-men}).
+Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:best-men}).
 Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.

### 2016-02-29 paper.tex
Matt

--- 2016-02-29 paper.tex
@@
 As intransitive verbs and adjectives have  tensors of rank 2,  transitive verbs  rank 3, and prepositions rank 7,
-if one takes $n= \textbf{30k}$ one will end up with   spaces with intractable dimensions  $\textbf{30}^\textbf{2} \textbf{k}$, $\textbf{30}^\textbf{3} \textbf{k}$ and $\textbf{30}^\textbf{7} \textbf{k}$.
+taking $n= \textbf{30K}$ results in spaces with intractable dimensions  $\textbf{30K}^\textbf{2}$, $\textbf{30K}^\textbf{3}$ and $\textbf{30K}^\textbf{7}$.
 
@@
 \end{equation}
-
+%
 PMI in its raw form is problematic: non-observed co-occurrences lead to infinite PMI values, making it impossible to compute similarity.
 A common ``fix'' to this problem is to replace all infinities with zeroes, and we use PMI hereafter to refer to a weighting with this fix.
-
+%
 An alternative solution is to increment the probability ratio by 1; we refer to this as \textit{compressed PMI} (CPMI):
@@
 We experiment with $\alpha$ values of 1 (no smoothing) and 0.75.
-We refer to this estimation method as \emph{local context probability}; we can also estimate a \emph{global context probability} based on global context appearance:
+We refer to this estimation method as \emph{local context probability}; we can also estimate a \emph{global context probability} based on the size of the corpus $C$:
 %
@@
 %
-where $|C|$ is the size of the used corpus.
+%where $|C|$ is the size of the used corpus.
 
@@
 PMI should be used with global context probabilities.
-\NCPMI/ and \logNCPMI/ should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
+CPMI generally outperforms PMI, with less sensitivity to parameters; \NCPMI/ and \logNCPMI/ should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
 
@@
 
-We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search for each dimensionality choice); and the best models reported by \cite{TACL570} (see Figure~\ref{fig:simlex-ppmi-best-simlex}).
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:simlex-ppmi-best-simlex}.
 
@@
 
-Heuristics for \logNSCPMI/and \SCPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as well as others.
+Heuristics for \logNSCPMI/ and \SCPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as well as others.
 

### 2016-02-29 paper.tex

@@
 
-We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:simlex-ppmi-best-simlex}.
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex}.
 

### 2016-02-29 figures/best.tex
Pre-submission.

@@
     \includegraphics[width=\textwidth]{supplement/figures/SimLex999-best}
-    \caption{\textbf{SimLex-999.} The black line refers to the score of 0.393. \\
+    \caption{\scriptsize \textbf{SimLex-999.} Black line: 0.393.
       This work: 0.385,
@@
     \includegraphics[width=\textwidth]{supplement/figures/SimLex999-global-best}
-    \caption{\textbf{SimLex-999.}
-    }
+    \caption{}
     \label{fig:global-best-simlex}
@@
     \includegraphics[width=\textwidth]{supplement/figures/men-best}
-    \caption{\textbf{MEN.} The black line refers to the score of 0.745. \\
+    \caption{\scriptsize \textbf{MEN.} Black line: 0.745.
       This work: 0.765,
@@
     \includegraphics[width=\textwidth]{supplement/figures/men-global-best}
-    \caption{\textbf{MEN.}
-    }
+    \caption{}
     \label{fig:global-best-men}
@@
 
-  \caption{\textbf{Best configurations.} Black line shows the best count models reported by \protect\newcite{TACL570}.
-We also give our best score, SGNS and GloVe numbers from that study for comparison.}
+  \caption{\small\textbf{Best configurations.} The black lines show the best count models reported by \protect\newcite{TACL570}.
+We also give our best score, SGNS and GloVe numbers from that study for comparison.
+On the right, our heuristic in comparison to the best and average results together with the models selected using the recommendations presented in \protect\newcite{TACL570}.}
   \label{fig:best}

### 2016-02-29 paper.tex
Pre-submission.

@@
 In contrast, much work on \emph{compositional} distributional semantics employs vectors with much fewer dimensions: e.g.~\textbf{2K} \cite{Grefenstette:2011:ESC:2145432.2145580,kartsadrqpl2014,milajevs-EtAl:2014:EMNLP2014}, \textbf{3K} \cite{Dinu:2010:MDS:1870658.1870771,milajevs-purver:2014:CVSC} or \textbf{10K} \cite{polajnar-clark:2014:EACL,Baroni2010nouns}.
-These models  assign tensors to functional words; for a vector space $V$ with dimension $k$,  a tensor $V \otimes V \cdots \otimes V$ of rank $n$ has dimension  $n^k$.
-As intransitive verbs and adjectives have  tensors of rank 2,  transitive verbs  rank 3, and prepositions rank 7,
-taking $n= \textbf{30K}$ results in spaces with intractable dimensions  $\textbf{30K}^\textbf{2}$, $\textbf{30K}^\textbf{3}$ and $\textbf{30K}^\textbf{7}$.
-
+The most common reason thereof is that these models  assign tensors to functional words.
+For a vector space $V$ with $k$ dimensions,  a tensor $V \otimes V \cdots \otimes V$ of rank $n$ has $k^n$ dimensions.
+Adjectives and intransitive verbs have tensors of rank 2, transitive verbs are of rank 3; for coordinators, the rank can go up to 7.
+Taking $k = \textbf{200K}$ already results in a highly intractable tensor of $\textbf{8} \times \textbf{10}^{\textbf{15}}$ dimensions for a transitive verb.
+%
 This mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
@@
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence performance of high-dimensional and low-dimensional models in the same way? Can the findings of \newcite{TACL570} be directly applied to low-dimensional models?
+\item Do parameters influence high-dimensional and low-dimensional models similarly? Can the findings of \newcite{TACL570} be directly applied to low-dimensional models?
 \item If not, can we derive suitable parameter selection heuristics which take account of dimensionality?
@@
 %
-PMI in its raw form is problematic: non-observed co-occurrences lead to infinite PMI values, making it impossible to compute similarity.
+%PMI in its raw form is problematic: non-observed co-occurrences lead to infinite PMI values, making it impossible to compute similarity.
 A common ``fix'' to this problem is to replace all infinities with zeroes, and we use PMI hereafter to refer to a weighting with this fix.
+%
+As commonly done, we replace the infinite PMI values with zeroes and use PMI hereafter to refer to a
+weighting with this fix.
 %
@@
 Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance \cite{Turney:2010:FMV:1861751.1861756}.
-This can be generalised as an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
+This can be generalised to an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
 %
@@
 where $n(x, y)$ is the number of times $x$ was seen together with $y$.
-For clarity, we refer to $n$-weighted PMIs as \NPMI/, \NSPMI/, \NCPMI/ and \NSCPMI/.
-When this weighting component is set to 1, it has no effect; we can  explicitly label this \PMI/, \SPMI/, \CPMI/ and \SCPMI/.
+For clarity, we refer to $n$-weighted PMIs as \NPMI/, \NSPMI/, etc.
+When this weighting component is set to 1, it has no effect; we can  explicitly label it as \PMI/, \SPMI/, etc.
 
-In addition to $1$ and $n$ weightings, we experiment with a $\log n$ weighting.
+In addition to the extreme $1$ and $n$ weightings, we also experiment with a $\log n$ weighting.
 % \textbf{MP: cite ref for this?}
@@
 %
-We experiment with $\alpha$ values of 1 (no smoothing) and 0.75.
-We refer to this estimation method as \emph{local context probability}; we can also estimate a \emph{global context probability} based on the size of the corpus $C$:
+We experiment with $\alpha$=1 (no smoothing) and $\alpha$=0.75.
+We call this estimation method \emph{local context probability}; we can also estimate a \emph{global context probability} based on the size of the corpus $C$:
 %
@@
 
-\subsection{Vector dimensionality}
+\subsection{Vector dimensionality ($D$)}
 \label{sec:vect-dimens}
@@
 All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.
-transitive vs.
-ditransitive versions of verbs).
+intransitive vs.
+transitive versions of verbs).
 
@@
 
-Table~\ref{tab:parameters} lists parameters used in this work and their values.
-As the source corpus we use the concatenation of Wackypedia and ukWaC \cite{Baroni2009} using a symmetric window of 5 words (following \newcite{milajevs-EtAl:2014:EMNLP2014}); our evaluation metric is the correlation with human judgements as standardly used with SimLex \cite{hill2014simlex}.
-We derive our parameter selection heuristics by greedily selecting parameters (\texttt{cds} and \texttt{neg}) that lead to the highest average performance for each combination of frequency weighting, PMI variant and dimensionality.
+Table~\ref{tab:parameters} lists parameters and their values.
+As the source corpus we use the concatenation of Wackypedia and ukWaC \cite{Baroni2009} with a symmetric 5-word window \cite{milajevs-EtAl:2014:EMNLP2014}; our evaluation metric is the correlation with human judgements as is standard with SimLex \cite{hill2014simlex}.
+We derive our parameter selection heuristics by greedily selecting parameters (\texttt{cds}, \texttt{neg}) that lead to the highest average performance for each combination of frequency weighting, PMI variant and dimensionality $D$.
 Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show the interaction of \texttt{cds} and \texttt{neg} with other parameters.
-We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report detailed results due to limited space.
+We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report results here due to space limits.
 
@@
 10K dimensional \SPMI/ is the least sensitive to parameter selection.
-For models with dimensionality greater than 20K, context distribution smoothing should be used with $\alpha = 0.75$.
-For models with dimensionality lower than 20K, it is beneficial to use global context probabilities.
-Shifting also depends on the dimensionality: models with up to 20K dimensions should set $k = 0.7$ and models with a higher number of dimensions should set $k = 5$.
-Note, however, that there might be a finer grained $k$ selection criteria, which we do not report in order to avoid overfitting.
+For models with $D>$ 20K, context distribution smoothing should be used with $\alpha = 0.75$; for $D<$ 20K, it is beneficial to use global context probabilities.
+Shifting also depends on the dimensionality: models with $D<$ 20K should set $k = 0.7$, but higher-dimensional models should set $k = 5$.
+There might be a finer-grained $k$ selection criteria; however, we do not report this to avoid overfitting.
 
@@
 
-\logNSPMI/ should be used with global context probabilities for models with vector dimensions up to 20K.
-For more dimensional spaces, smoothing should be applied with $\alpha = 0.75$, which is similar to \SPMI/.
-Shifting should be applied with $k = 0.5$ for models with less than 20K dimensions and $k = 1.4$ for models with more than 20K dimensions.
-In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $k = 1.4$ is a much robust choice for \logNSPMI/.
+\logNSPMI/ should be used with global context probabilities for models with $D<$ 20K.
+For higher-dimensional spaces, smoothing should be applied with $\alpha = 0.75$, as with \SPMI/.
+Shifting should be applied with $k = 0.5$ for models with $D<$ 20K,  and $k = 1.4$ for $D>$ 20K.
+In contrast to \SPMI/, which might require change of $k$ as the dimensionality increases, $k = 1.4$ is a much more robust choice for \logNSPMI/.
 
-\NSPMI/ gives good results with local context probabilities ($\alpha = 1$). Models with less than 20K dimensions should be used with $k = 1.4$, otherwise $k = 5$ should be preferred.
+\NSPMI/ gives good results with local context probabilities ($\alpha = 1$). Models with $D<$ 20K  should use $k = 1.4$, otherwise $k = 5$ is preferred.
 
@@
 
-With \SCPMI/ and vector dimensionality less than 20K, global context probability should be used and shifting should be set to $k = 0.7$.
-Otherwise, local context probability should be used with $\alpha = 0.75$ and $k = 2$.
+With \SCPMI/ and $D<$ 20K, global context probability should be used, with shifting set to $k = 0.7$. Otherwise, local context probability should be used with $\alpha = 0.75$ and $k = 2$.
 
-With \NSCPMI/ and dimensions less than 20K, global context probability should be used with $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.
+With \NSCPMI/ and $D<$ 20K, global context probability should be used with $k = 1.4$. Otherwise, local context probability without smoothing and $k = 5$ is suggested.
 
-For \logNSCPMI/, models with less than 20K dimensions should be used with global context probabilities and $k = 0.7$; otherwise, local context probabilities without smoothing should be preferred with $k = 1.4$.
+For \logNSCPMI/, models with $D<$ 20K should use global context probabilities and $k = 0.7$; otherwise, local context probabilities without smoothing should be preferred with $k = 1.4$.
 
@@
 
-We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting); as well as the best scores reported by \cite{TACL570}, and those given by word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex}.
+We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting).
+We also compare them to the best scores reported by \cite{TACL570} for their model, word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
 
 For \logNPMI/ and \logNCPMI/, our heuristics pick the best possible models.
-For \logNSPMI/, where performance variance is low, the heuristics do well, giving performance no more than 0.01 points below the best configuration.
-For \SPMI/ and \NSPMI/ this difference is much higher.
+For \logNSPMI/, where performance variance is low, the heuristics do well, giving a performance of no more than 0.01 points below the best configuration.
+For \SPMI/ and \NSPMI/ the difference is higher.
+With \logNSCPMI/ and \SCPMI/, the heuristics follow the best selection, but with a wider gap than the SPMI models.
+In general $n$-weighted models do not perform as well as others.
 
-Heuristics for \logNSCPMI/ and \SCPMI/ follow the best selection, but with a wider gap than the SPMI models. In general $n$ weighted models do not perform as well as others.
+Overall, $\log n$ weighting should be used with PMI, CPMI and SCPMI.
+High-dimensional SPMI models show the same behaviour, but if $D<$ 10K, no weighting should be applied.
+SPMI and SCPMI should be preferred over CPMI and PMI.
+As Figure~\ref{fig:global-best-simlex} shows, our heuristics give performance close to the optimum for any dimensionality, with a large improvement over both an average parameter setting and the parameters suggested by \cite{TACL570} in a high-dimensional setting.\footnote{Our results using \cite{TACL570}'s parameters differ slightly from theirs due to different window sizes (5 vs 2).}
 
-$\log n$ weighting should be used with PMI, CPMI and SCPMI.
-High-dimensional SPMI models show the same behaviour, but if vector dimensionality is less than 10K, no weighting should be applied.
-SPMI and SCPMI should be preferred over CPMI and PMI.
-
-Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figure~\ref{fig:best-men}).
-Again, PMI and CPMI follow the best possible setup and there is a little gap between the chosen models and the best possible selection for SPMI and SCPMI.
+Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figures~\ref{fig:best-men},\ref{fig:global-best-men}).
+Again, PMI and CPMI follow the best possible setup, with SPMI and SCPMI showing only a slight drop below ideal performance; and again, the heuristic settings give performance close to the optimum, and significantly higher than average or standard parameters.
 
@@
 
-This paper presents a systematic study of co-occurrence quantification focusing of the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low-dimensional spaces.
-As an outcome of such an analysis we propose a set of model selection heuristics that maximize performance.
+This paper presents a systematic study of co-occurrence quantification focusing on the selection of parameters presented in \newcite{TACL570}.
+We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low-dimensional spaces, and propose a set of model selection heuristics that maximizes performance.
 
@@
 However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.
-Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.
+Based on this we suggest the use of \logNSPMI/ or \logNSCPMI/ with dimensionality of at least 20K to ensure good performance on lexical tasks.
 

### 2016-04-26 paper.tex
Submission
Pre Student ACL

@@
 
-\title{Robust co-occurrence quantification for low-dimensional lexical distributional semantics}
+\title{Robust Co-occurrence Quantification for Lexical Distributional Semantics}
 
@@
 \begin{document}
-\def\emnlp/{\textit{KS2013}}
-\def\PhraseRel/{PhraseRel}
 
-\def\PMI/{$1 \operatorname{PMI}$}
-\def\SPMI/{$1 \operatorname{SPMI}$}
-\def\CPMI/{$1 \operatorname{CPMI}$}
-\def\SCPMI/{$1 \operatorname{SCPMI}$}
+\def\PMI/{$\operatorname{1PMI}$}
+\def\SPMI/{$\operatorname{1SPMI}$}
+\def\CPMI/{$\operatorname{1CPMI}$}
+\def\SCPMI/{$\operatorname{1SCPMI}$}
 
-\def\NPMI/{$n \operatorname{PMI}$}
-\def\NSPMI/{$n \operatorname{SPMI}$}
-\def\NCPMI/{$n \operatorname{CPMI}$}
-\def\NSCPMI/{$n \operatorname{SCPMI}$}
+\def\NPMI/{$\operatorname{nPMI}$}
+\def\NSPMI/{$\operatorname{nSPMI}$}
+\def\NCPMI/{$\operatorname{nCPMI}$}
+\def\NSCPMI/{$\operatorname{nSCPMI}$}
 
-\def\logNPMI/{$\log n\operatorname{PMI}$}
-\def\logNSPMI/{$\log n\operatorname{SPMI}$}
-\def\logNCPMI/{$\log n \operatorname{CPMI}$}
-\def\logNSCPMI/{$\log n \operatorname{SCPMI}$}
+\def\logNPMI/{$\operatorname{lognPMI}$}
+\def\logNSPMI/{$\operatorname{lognSPMI}$}
+\def\logNCPMI/{$\operatorname{lognCPMI}$}
+\def\logNSCPMI/{$\operatorname{lognSCPMI}$}
 
@@
 \begin{abstract}
-\input{abstract.tex}
+Previous optimisations of parameters affecting the word-context association measure used in distributional vector space models have focused either on high-dimensional vectors with hundreds of thousands of dimensions, or dense vectors with dimensionality of few hundreds; but dimensionality of few thousands is often applied in compositional tasks as it is still computationally feasible and does not require the dimensionality reduction step.
+We present a systematic study of the interaction of the parameters of the association measure and vector dimensionality, and derive parameter selection heuristics that achieve performance across word similarity and relevance datasets competitive with the results previously reported in the literature achieved by highly dimensional or dense models.
 \end{abstract}
@@
 
-\newcite{TACL570} propose optimisations for co-occrrence-based distributional models, using parameters adopted from predictive models \cite{mikolov2013efficient}: \emph{shifting} and \emph{context distribution smoothing}.
+\newcite{TACL570} propose optimisations for co-occurrence-based distributional models, using parameters adopted from predictive models \cite{mikolov2013efficient}: \emph{shifting} and \emph{context distribution smoothing}.
 Their experiments and thus their parameter  recommendations use high-dimensional vector spaces with word vector dimensionality of almost \textbf{200K}, and many recent state-of-the-art results in lexical distributional semantics have been obtained using vectors with similarly high dimensionality  \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
@@
 Taking $k = \textbf{200K}$ already results in a highly intractable tensor of $\textbf{8} \times \textbf{10}^{\textbf{15}}$ dimensions for a transitive verb.
-%
-This mismatch in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
+
+An alternative way of obtaining a vector space with few dimensions, usually with just 100--500, is to use SVD as a part of Latent Semantic Analysis \cite{ARIS:ARIS1440380105} or another models such as SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}.
+However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix and bring more parameters to explore.
+In this work we focus on vector spaces that directly weight a co-occurrence matrix and report results for SVD, GloVe and SGNS from the study of \newcite{TACL570} for comparison.
+
+\input{figures/interaction-neg}
+
+The mismatch of experiments with non-dense models in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
 \begin{compactitem}
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence high-dimensional and low-dimensional models similarly? Can the findings of \newcite{TACL570} be directly applied to low-dimensional models?
+\item Do parameters influence 200K and 1K dimensional models similarly? Can the findings of \newcite{TACL570} be directly applied to models with few thousand dimensions?
 \item If not, can we derive suitable parameter selection heuristics which take account of dimensionality?
@@
 In addition to the extreme $1$ and $n$ weightings, we also experiment with a $\log n$ weighting.
-% \textbf{MP: cite ref for this?}
-
-\input{figures/interaction-neg}
 
@@
 %
-We experiment with $\alpha$=1 (no smoothing) and $\alpha$=0.75.
+We experiment with $\alpha$=1 (no smoothing) and $\alpha = 0.75$.
 We call this estimation method \emph{local context probability}; we can also estimate a \emph{global context probability} based on the size of the corpus $C$:
@@
 \end{equation}
-%
-%where $|C|$ is the size of the used corpus.
 
@@
 We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting).
-We also compare them to the best scores reported by \cite{TACL570} for their model, word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
+We also compare them to the best scores reported by \newcite{TACL570} for their model, word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
 
@@
 
-Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figures~\ref{fig:best-men},\ref{fig:global-best-men}).
+Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figures~\ref{fig:best-men}, \ref{fig:global-best-men}).
 Again, PMI and CPMI follow the best possible setup, with SPMI and SCPMI showing only a slight drop below ideal performance; and again, the heuristic settings give performance close to the optimum, and significantly higher than average or standard parameters.
 
-% \textbf{MP: is it worth including a line for the *worst* possible parameter selection too?
-Or for the average; or for the Levy/Goldberg "standard" parameters?
-That way the reader can see how much benefit the heuristics give.
-}
+\begin{table}
+  \centering
+  \begin{tabular}{lll}
+    \toprule
+    Model           & SimLex-999 & MEN \\
+    \midrule
+    PPMI$^*$        & 0.393      & 0.745 \\
+    SVD$^*$         & 0.432      & 0.778 \\
+    SGNS$^*$        & 0.438      & 0.774 \\
+    GloVe$^*$       & 0.398      & 0.729 \\
+    \addlinespace
+    This work       & 0.385      & 0.765 \\
+    \bottomrule
+  \end{tabular}
+  \caption{\textbf{Results.} Our model in comparison to the previous work.
+On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above, note the difference in dimensionality and source corpora, and window size.
+SVD and SGNS and GloVe numbers are given for comparison.
+$^*$Results reported by \newcite{TACL570}.}
+\label{tab:results}
+\end{table}
 
@@
 This paper presents a systematic study of co-occurrence quantification focusing on the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with low-dimensional spaces, and propose a set of model selection heuristics that maximizes performance.
+We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with spaces of dimensionallity of 1K to 50K, and propose a set of model selection heuristics that maximizes performance.
+We foresee the results of the paper are generalisable to other experiments, since model selection was performed on a similarity dataset, and was additionally tested on a relatedness dataset.
 
 In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-Low-dimensional spaces benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
+Spaces with few thousand dimensions benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
 However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.

### 2016-04-26 figures/best.tex

@@
     \includegraphics[width=\textwidth]{supplement/figures/SimLex999-best}
-    \caption{\scriptsize \textbf{SimLex-999.} Black line: 0.393.
-      This work: 0.385,
+    \caption{\scriptsize \textbf{SimLex-999.}
+      PPMI: 0.393.
+      SVD: 0.432,
       SGNS: 0.438,
       GloVe: 0.398.
+      This work: 0.385,
     }
@@
     \includegraphics[width=\textwidth]{supplement/figures/men-best}
-    \caption{\scriptsize \textbf{MEN.} Black line: 0.745.
-      This work: 0.765,
+    \caption{\scriptsize \textbf{MEN.}
+      PPMI: 0.745.
+      SVD: 0.778,
       SGNS: 0.774,
       GloVe: 0.729.
+      This work: 0.765,
     }
@@
 
-  \caption{\small\textbf{Best configurations.} The black lines show the best count models reported by \protect\newcite{TACL570}.
-We also give our best score, SGNS and GloVe numbers from that study for comparison.
+  \caption{\small\textbf{Best configurations.} The black lines show the best count models (PPMI) reported by \protect\newcite{TACL570}.
+We also give our best score, SVD, SGNS and GloVe numbers from that study for comparison.
 On the right, our heuristic in comparison to the best and average results together with the models selected using the recommendations presented in \protect\newcite{TACL570}.}

### 2016-05-31 paper.tex
Final changes

@@
 \usepackage{adjustbox}
+\usepackage{url}
 
-\makeatletter
-\newcommand{\@BIBLABEL}{\@emptybiblabel}
-\newcommand{\@emptybiblabel}[1]{}
-\makeatother
+% \makeatletter
+% \newcommand{\@BIBLABEL}{\@emptybiblabel}
+% \newcommand{\@emptybiblabel}[1]{}
+% \makeatother
 % \usepackage{hyperref}
 
-\sloppy
+% \sloppy
 
-% \aclfinalcopy % Uncomment this line for the final submission
-\def\aclpaperid{34} %  Enter the acl Paper ID here
+\aclfinalcopy % Uncomment this line for the final submission
+\def\aclpaperid{30} %  Enter the acl Paper ID here
 
@@
 
-% \author{First Author \\
-%   Affiliation / Address line 1 \\
-%   Affiliation / Address line 2 \\
-%   Affiliation / Address line 3 \\
-%   {\tt email@domain} \\\And
-%   Second Author \\
-%   Affiliation / Address line 1 \\
-%   Affiliation / Address line 2 \\
-%   Affiliation / Address line 3 \\
-%   {\tt email@domain} \\}
-
+\author{Dmitrijs Milajevs\qquad{}Mehrnoosh Sadrzadeh\qquad{}Matthew Purver\\
+  Queen Mary University of London\\
+  London, UK\\
+  {\tt \{d.milajevs,m.sadrzadeh,m.purver\}@qmul.ac.uk}
+}
 \date{}
@@
 
-An alternative way of obtaining a vector space with few dimensions, usually with just 100--500, is to use SVD as a part of Latent Semantic Analysis \cite{ARIS:ARIS1440380105} or another models such as SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}.
+An alternative way of obtaining a vector space with few dimensions, usually with just 100--500, is the use of SVD as a part of Latent Semantic Analysis \cite{ARIS:ARIS1440380105} or another models such as SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}.
 However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix and bring more parameters to explore.
@@
 
-To answer these, we perform a systematic study of distributional models with a rich set of parameters on two lexical datasets: SimLex-999 \cite{hill2014simlex} and MEN \cite{Bruni:2014:MDS:2655713.2655714}.
+To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset.
 
@@
 As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
-All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.
-intransitive vs.
+All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.
 transitive versions of verbs).
@@
 Figures~\ref{fig:interaction-cds} and \ref{fig:interaction-neg} show the interaction of \texttt{cds} and \texttt{neg} with other parameters.
-We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report results here due to space limits.
+We also vary the similarity measure (cosine and correlation  \cite{kiela-clark:2014:CVSC}), but do not report results here due to space limits.\footnotemark{}
+
+\footnotetext{The results are available at \url{http://www.eecs.qmul.ac.uk/~dm303/aclsrw2016/}}
 
@@
 10K dimensional \SPMI/ is the least sensitive to parameter selection.
-For models with $D>$ 20K, context distribution smoothing should be used with $\alpha = 0.75$; for $D<$ 20K, it is beneficial to use global context probabilities.
-Shifting also depends on the dimensionality: models with $D<$ 20K should set $k = 0.7$, but higher-dimensional models should set $k = 5$.
+For models with $D>$~20K, context distribution smoothing should be used with $\alpha = 0.75$; for $D<$~20K, it is beneficial to use global context probabilities.
+Shifting also depends on the dimensionality: models with $D<$~20K should set $k = 0.7$, but higher-dimensional models should set $k = 5$.
 There might be a finer-grained $k$ selection criteria; however, we do not report this to avoid overfitting.
@@
 
-\logNSPMI/ should be used with global context probabilities for models with $D<$ 20K.
+\logNSPMI/ should be used with global context probabilities for models with $D<$~20K.
 For higher-dimensional spaces, smoothing should be applied with $\alpha = 0.75$, as with \SPMI/.
@@
 
-\NSPMI/ gives good results with local context probabilities ($\alpha = 1$). Models with $D<$ 20K  should use $k = 1.4$, otherwise $k = 5$ is preferred.
+\NSPMI/ gives good results with local context probabilities ($\alpha = 1$). Models with $D<$~20K  should use $k = 1.4$, otherwise $k = 5$ is preferred.
 
@@
 We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting).
-We also compare them to the best scores reported by \newcite{TACL570} for their model, word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
+We also compare them to the best scores reported by \newcite{TACL570} for their model (PMI and SVD), word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
 
@@
   \end{tabular}
-  \caption{\textbf{Results.} Our model in comparison to the previous work.
-On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above, note the difference in dimensionality and source corpora, and window size.
-SVD and SGNS and GloVe numbers are given for comparison.
+  \caption{\textbf{Our model in comparison to the previous work.} On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above.
+Note the difference in dimensionality and source corpora, and window size.
+SVD, SGNS and GloVe numbers are given for comparison.
 $^*$Results reported by \newcite{TACL570}.}
@@
 This paper presents a systematic study of co-occurrence quantification focusing on the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with spaces of dimensionallity of 1K to 50K, and propose a set of model selection heuristics that maximizes performance.
+We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with spaces of dimensionality of 1K to 50K, and propose a set of model selection heuristics that maximizes performance.
 We foresee the results of the paper are generalisable to other experiments, since model selection was performed on a similarity dataset, and was additionally tested on a relatedness dataset.
@@
 Spaces with few thousand dimensions benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
-However, these heuristics do not guarantee the best possible result for unweighted and $n$-weighted models because of the high variance of the corresponding scores.
-Based on this we suggest the use of \logNSPMI/ or \logNSCPMI/ with dimensionality of at least 20K to ensure good performance on lexical tasks.
+However, for unweighted and $n$-weighted models, these heuristics do not guarantee the best possible result because of the high variance of the corresponding scores.
+Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with dimensionality of at least 20K to ensure good performance on lexical tasks.
 
-%\bibliographystyle{acl}
-% remove publisher, month etc from conf proceedings:
-% \bibliographystyle{acl-short}
+\section{Acknowledgements}
+
+We thank the anonymous reviewers for their comments. Support from EPSRC grant EP/J002607/1 is gratefully acknowledged by Milajevs and Sadrzadeh..
+Purver is partly supported by ConCreTe: the project ConCreTe acknowledges the financial support of the Future and Emerging Technologies (FET) programme within the Seventh Framework Programme for Research of the European Commission, under FET grant number 611733.
+
 \bibliographystyle{acl2016}

### 2016-05-31 paper.tex
Intro

@@
 \label{sec:introduction}
+
+Words that occur in similar context have similar meaning \cite{harris1954distributional}.
+Thus the meaning of a word can be modeled by counting its co-occurrence with neighboring words in a corpus.
+Distributional models of meaning represent co-occurrence information in a vector space, where the dimensions are the neighboring words and the values are co-occurrence counts.
+Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with a word \textit{existence}.
+Another fundamental question is the vector space dimensionality and what neighbor words correspond to them.
 

### 2016-05-31 paper.tex
Layout
Minor

@@
 Distributional models of meaning represent co-occurrence information in a vector space, where the dimensions are the neighboring words and the values are co-occurrence counts.
-Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with a word \textit{existence}.
-Another fundamental question is the vector space dimensionality and what neighbor words correspond to them.
+Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with the noun \textit{existence}.
+Another fundamental question is the vector space dimensionality and what neighbor words should correspond to them.
 
@@
 In this work we focus on vector spaces that directly weight a co-occurrence matrix and report results for SVD, GloVe and SGNS from the study of \newcite{TACL570} for comparison.
-
-\input{figures/interaction-neg}
 
@@
 As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
-All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.
-transitive versions of verbs).
+All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.~transitive versions of verbs).
 
@@
 
+\input{figures/interaction-neg}
+
 \paragraph{SPMI}
@@
 There might be a finer-grained $k$ selection criteria; however, we do not report this to avoid overfitting.
-
-\input{figures/best}
 
@@
 
+\input{figures/best}
+
 Finally, to see whether the heuristics transfer robustly, we repeat this comparison on the MEN dataset (see Figures~\ref{fig:best-men}, \ref{fig:global-best-men}).
@@
   \caption{\textbf{Our model in comparison to the previous work.} On the similarity dataset our model is 0.008 points behind a PPMI model, however on the relatedness dataset 0.020 points above.
-Note the difference in dimensionality and source corpora, and window size.
+Note the difference in dimensionality, source corpora and window size.
 SVD, SGNS and GloVe numbers are given for comparison.
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 

### 2016-06-07 paper.tex
Minor changes

@@
 %
-As commonly done, we replace the infinite PMI values with zeroes and use PMI hereafter to refer to a
-weighting with this fix.
+As commonly done, we replace the infinite PMI values with zeroes and use PMI hereafter to refer to a weighting with this fix.
 %
@@
 %
-We experiment with $\alpha$=1 (no smoothing) and $\alpha = 0.75$.
+We experiment with $\alpha=1$ (no smoothing) and $\alpha = 0.75$.
 We call this estimation method \emph{local context probability}; we can also estimate a \emph{global context probability} based on the size of the corpus $C$:
@@
 
-We thank the anonymous reviewers for their comments. Support from EPSRC grant EP/J002607/1 is gratefully acknowledged by Milajevs and Sadrzadeh..
+We thank the anonymous reviewers for their comments. Support from EPSRC grant EP/J002607/1 is gratefully acknowledged by Milajevs and Sadrzadeh.
 Purver is partly supported by ConCreTe: the project ConCreTe acknowledges the financial support of the Future and Emerging Technologies (FET) programme within the Seventh Framework Programme for Research of the European Commission, under FET grant number 611733.

### 2016-06-07 figures/interaction-cds.tex
Matt
Mentoring comments

@@
     \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-cds}}
-    \caption{\textbf{The effect of context probability estimation and smoothing on SimLex-999.}}
+    \caption{{\bf Effect of PMI variant (\texttt{discr}), smoothing (\texttt{cds}) and frequency weighting (\texttt{freq}) on SimLex-999.} Error bars correspond to a 95\% confidence interval as the value is estimated by aggregating over omitted parameters: \texttt{neg} and similarity.}
     \label{fig:interaction-cds}

### 2016-06-07 paper.tex
Mentoring comments

@@
 
-\aclfinalcopy % Uncomment this line for the final submission
+% \aclfinalcopy % Uncomment this line for the final submission
 \def\aclpaperid{30} %  Enter the acl Paper ID here
@@
 \begin{abstract}
-Previous optimisations of parameters affecting the word-context association measure used in distributional vector space models have focused either on high-dimensional vectors with hundreds of thousands of dimensions, or dense vectors with dimensionality of few hundreds; but dimensionality of few thousands is often applied in compositional tasks as it is still computationally feasible and does not require the dimensionality reduction step.
+Previous optimisations of parameters affecting the word-context association measure used in distributional vector space models have focused either on high-dimensional vectors with hundreds of thousands of dimensions, or dense vectors with dimensionality of a few hundreds; but dimensionality of a few thousands is often applied in compositional tasks as it is still computationally feasible and does not require the dimensionality reduction step.
 We present a systematic study of the interaction of the parameters of the association measure and vector dimensionality, and derive parameter selection heuristics that achieve performance across word similarity and relevance datasets competitive with the results previously reported in the literature achieved by highly dimensional or dense models.
@@
 An alternative way of obtaining a vector space with few dimensions, usually with just 100--500, is the use of SVD as a part of Latent Semantic Analysis \cite{ARIS:ARIS1440380105} or another models such as SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}.
-However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix and bring more parameters to explore.
+However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix, bring more parameters to explore and produce vector spaces with uninterpretable dimensions.
 In this work we focus on vector spaces that directly weight a co-occurrence matrix and report results for SVD, GloVe and SGNS from the study of \newcite{TACL570} for comparison.
@@
 \item To what extent does model performance depend on vector dimensionality?
-\item Do parameters influence 200K and 1K dimensional models similarly? Can the findings of \newcite{TACL570} be directly applied to models with few thousand dimensions?
+\item Do parameters influence 200K and 1K dimensional models similarly? Can the findings of \newcite{TACL570} be directly applied to models with a few thousand dimensions?
 \item If not, can we derive suitable parameter selection heuristics which take account of dimensionality?
@@
 To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset.
+Both datasets are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and quality by attention to evaluated relation.
 
@@
 
-Most co-occurrence weighting schemes in distributional semantics are based on \emph{point-wise mutual information} (PMI, Equation~\ref{eq:pmi}) (see e.g.~\newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756}, \newcite{NIPS2014_5477}).
+Most co-occurrence weighting schemes in distributional semantics are based on \emph{point-wise mutual information} (PMI, see e.g.~\newcite{J90-1003}, \newcite{Turney:2010:FMV:1861751.1861756}, \newcite{NIPS2014_5477}):
 %
@@
 %
-%PMI in its raw form is problematic: non-observed co-occurrences lead to infinite PMI values, making it impossible to compute similarity.
-A common ``fix'' to this problem is to replace all infinities with zeroes, and we use PMI hereafter to refer to a weighting with this fix.
-%
-As commonly done, we replace the infinite PMI values with zeroes and use PMI hereafter to refer to a weighting with this fix.
-%
-An alternative solution is to increment the probability ratio by 1; we refer to this as \textit{compressed PMI} (CPMI):
+As commonly done, we replace the infinite PMI values,\footnotemark{} which arise when $P(x, y) = 0$, with zeroes and use PMI hereafter to refer to a weighting with this fix.
+
+\footnotetext{We assume that the probability of a single token is always greater than zero as it appears in the corpus at least once.}
+
+An alternative solution is to increment the probability ratio by 1; we refer to this as \textit{compressed PMI} (CPMI, see e.g.~\newcite{McGregorEtAl15JAGI}):
 %
@@
 
+By incrementing the probability ratio by one, the PMI values from the segment of $(-\infty$; 0], when the joint probability $P(x,y)$ is less than the chance $P(x)P(y)$, are compressed into the segment of $(0; 1]$.
+As the result, the space does not contain negative values, but has the same sparsity as the space with PMI values.
+% In our experiments with spaces containing 56 thousand target words,
+
 \input{figures/parameters}
@@
 
-Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance \cite{Turney:2010:FMV:1861751.1861756}.
+Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance and sparser matrices are more computationally tractable \cite{Turney:2010:FMV:1861751.1861756}.
 This can be generalised to an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
@@
 %
+When $k = 1$ SPMI is equivalent to positive PMI.
+$k > 1$ increases the underlying matrix sparsity by keeping only highly associated co-occurrence pairs.
+$k < 1$ decreases the underlying matrix sparsity by including some unassociated co-occurrence pairs, which are usually excluded due to unreliability of probability estimation \cite{Dagan:1993:CWS:981574.981596}.
+
 We can apply the same idea to CPMI:
@@
 As context words we select the 1K, 2K, 3K, 5K, 10K, 20K, 30K, 40K and 50K most frequent lemmatised nouns, verbs, adjectives and adverbs.
-All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.~transitive versions of verbs).
+All context words are part of speech tagged, but we do not distinguish between refined word types (e.g.~intransitive vs.~transitive versions of verbs) and do not perform stop word filtering.
 
@@
 SPMI and SCPMI should be preferred over CPMI and PMI.
-As Figure~\ref{fig:global-best-simlex} shows, our heuristics give performance close to the optimum for any dimensionality, with a large improvement over both an average parameter setting and the parameters suggested by \cite{TACL570} in a high-dimensional setting.\footnote{Our results using \cite{TACL570}'s parameters differ slightly from theirs due to different window sizes (5 vs 2).}
+As Figure~\ref{fig:global-best-simlex} shows, our heuristics give performance close to the optimum for any dimensionality, with a large improvement over both an average parameter setting and the parameters suggested by \cite{TACL570} in a high-dimensional setting.\footnote{Our results using \newcite{TACL570}'s parameters differ slightly from theirs due to different window sizes (5 vs 2).}
 
@@
 Again, PMI and CPMI follow the best possible setup, with SPMI and SCPMI showing only a slight drop below ideal performance; and again, the heuristic settings give performance close to the optimum, and significantly higher than average or standard parameters.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+This paper presents a systematic study of co-occurrence quantification focusing on the selection of parameters presented in \newcite{TACL570}.
+We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with spaces of dimensionality of 1K to 50K, and propose a set of model selection heuristics that maximizes performance.
+We foresee the results of the paper are generalisable to other experiments, since model selection was performed on a similarity dataset, and was additionally tested on a relatedness dataset.
+
+In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
+Spaces with a few thousand dimensions benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
+However, for unweighted and $n$-weighted models, these heuristics do not guarantee the best possible result because of the high variance of the corresponding scores.
+Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with dimensionality of at least 20K to ensure good performance on lexical tasks.
 
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
-
-This paper presents a systematic study of co-occurrence quantification focusing on the selection of parameters presented in \newcite{TACL570}.
-We replicate their recommendation for high-dimensional vector spaces, and show that with appropriate parameter selection it is possible to achieve comparable performance with spaces of dimensionality of 1K to 50K, and propose a set of model selection heuristics that maximizes performance.
-We foresee the results of the paper are generalisable to other experiments, since model selection was performed on a similarity dataset, and was additionally tested on a relatedness dataset.
-
-In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999).
-Spaces with few thousand dimensions benefit from being dense and unsmoothed  ($k < 1$, global context probability); while high-dimensional spaces are better sparse and smooth  ($k > 1$, $\alpha = 0.75$).
-However, for unweighted and $n$-weighted models, these heuristics do not guarantee the best possible result because of the high variance of the corresponding scores.
-Based on this we suggest to use \logNSPMI/ or \logNSCPMI/ with dimensionality of at least 20K to ensure good performance on lexical tasks.
-
 \section*{Acknowledgements}

### 2016-06-10 paper.tex
Updates from ShareLaTeX

@@
 
-% \aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 \def\aclpaperid{30} %  Enter the acl Paper ID here
@@
 
-%\renewcommand{\baselinestretch}{0.95}
+% \renewcommand{\baselinestretch}{0.95}
 
@@
 Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with the noun \textit{existence}.
-Another fundamental question is the vector space dimensionality and what neighbor words should correspond to them.
+The discrimination is usually achieved by weighting of co-occurrence counts.
+Another fundamental question in vector space design is the vector space dimensionality and what neighbor words should correspond to them.
 
@@
 An alternative way of obtaining a vector space with few dimensions, usually with just 100--500, is the use of SVD as a part of Latent Semantic Analysis \cite{ARIS:ARIS1440380105} or another models such as SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}.
-However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix, bring more parameters to explore and produce vector spaces with uninterpretable dimensions.
+However, these models take more time to instantiate in comparison to weighting of a co-occurrence matrix, bring more parameters to explore and produce vector spaces with uninterpretable dimensions (vector space dimension interpretation is used by some lexical models, for example, \newcite{McGregorEtAl15JAGI}, and the passage from formal semantics to tensor models relies on it \cite{DBLP:journals/corr/abs-1003-4394}).
 In this work we focus on vector spaces that directly weight a co-occurrence matrix and report results for SVD, GloVe and SGNS from the study of \newcite{TACL570} for comparison.
 
-The mismatch of experiments with non-dense models in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
+The mismatch of recent experiments with non-dense models in vector dimensionality between lexical and compositional tasks gives rise to a number of questions:
 \begin{compactitem}
@@
 To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset.
-Both datasets are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and quality by attention to evaluated relation.
+The reason for choosing these is that they are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and in quality by attention to evaluated relations.
 
@@
 Many approaches use only \emph{positive} PMI values, as  negative PMI values may not positively contribute to model performance and sparser matrices are more computationally tractable \cite{Turney:2010:FMV:1861751.1861756}.
-This can be generalised to an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):
+This can be generalised to an additional cutoff parameter $k$ (\texttt{neg}) following \newcite{TACL570}, giving our third PMI variant (abbreviated as SPMI):\footnotemark{}
 %
@@
 $k > 1$ increases the underlying matrix sparsity by keeping only highly associated co-occurrence pairs.
-$k < 1$ decreases the underlying matrix sparsity by including some unassociated co-occurrence pairs, which are usually excluded due to unreliability of probability estimation \cite{Dagan:1993:CWS:981574.981596}.
+$k < 1$ decreases the underlying matrix sparsity by including some unassociated co-occurrence pairs, which are usually excluded due to unreliability of probability estimates \cite{Dagan:1993:CWS:981574.981596}.
+
+\footnotetext{SPMI is different from CPMI because $\log\frac{P(x, y)}{P(x)P(y)} - \log{}k = \log\frac{P(x, y)}{P(x)(P(y)k} \neq \log\Big( 1 + \frac{P(x,y)}{P(x)P(y)} \Big)$.}
 
@@
 
-\section{Experiments}
+\input{figures/interaction-neg}
+
+\section{Experimental setup}
 \label{sec:lexical-experiments}
@@
 
+\section{Heuristics}
+
 \paragraph{PMI and CPMI}
@@
 CPMI generally outperforms PMI, with less sensitivity to parameters; \NCPMI/ and \logNCPMI/ should be used with local context probabilities and \CPMI/ should apply context distribution smoothing with $\alpha = 0.75$.
-
-\input{figures/interaction-neg}
 
@@
 
-\paragraph{Evaluation of heuristics}
+\input{figures/best}
+
+\section{Evaluation of heuristics}
 \label{sec:heuristic-evaluation}
@@
 We evaluate these heuristics by comparing the performance they give on SimLex-999 against that obtained using the best possible parameter selections (determined via an exhaustive search at each dimensionality setting).
-We also compare them to the best scores reported by \newcite{TACL570} for their model (PMI and SVD), word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove} -- see Figure~\ref{fig:best-simlex} (only the better-performing SPMI and SCPMI are shown).
+We also compare them to the best scores reported by \newcite{TACL570} for their model (PMI and SVD), word2vec-SGNS \cite{mikolov2013efficient} and GloVe \cite{pennington2014glove}---see Figure~\ref{fig:best-simlex}, where only the better-performing SPMI and SCPMI are shown.
 
@@
 SPMI and SCPMI should be preferred over CPMI and PMI.
-As Figure~\ref{fig:global-best-simlex} shows, our heuristics give performance close to the optimum for any dimensionality, with a large improvement over both an average parameter setting and the parameters suggested by \cite{TACL570} in a high-dimensional setting.\footnote{Our results using \newcite{TACL570}'s parameters differ slightly from theirs due to different window sizes (5 vs 2).}
-
-\input{figures/best}
+As Figure~\ref{fig:global-best-simlex} shows, our heuristics give performance close to the optimum for any dimensionality, with a large improvement over both an average parameter setting and the parameters suggested by \newcite{TACL570} in a high-dimensional setting.\footnote{Our results using \newcite{TACL570}'s parameters differ slightly from theirs due to different window sizes (5 vs 2).}
 
@@
 
+There are several directions for the future work.
+Our experiments show that models with a few thousand dimensions are competitive with more dimensional models, see Figure~\ref{fig:best}.
+Moreover, for these models, unsmoothed probabilities give the best result.
+It might be the case that due to the large size of the corpus used, the probability estimates for the most frequent words are reliable without smoothing.
+More experiments need to be done to see whether this holds for smaller corpora.
+
+The similarity datasets are transferred to other languages \cite{DBLP:journals/corr/LeviantR15}. The future work might investigate whether our results hold for languages other than English.
+
+The qualitative influence of the parameters should be studied in depth with extensive error analysis on how parameter selection changes similarity judgements.
+
 \section*{Acknowledgements}
 
-We thank the anonymous reviewers for their comments. Support from EPSRC grant EP/J002607/1 is gratefully acknowledged by Milajevs and Sadrzadeh.
-Purver is partly supported by ConCreTe: the project ConCreTe acknowledges the financial support of the Future and Emerging Technologies (FET) programme within the Seventh Framework Programme for Research of the European Commission, under FET grant number 611733.
+We thank Ann Copestake for her valuable comments as part of the ACL SRW mentorship program and the anonymous reviewers for their comments.
+Support from EPSRC grant EP/J002607/1 is gratefully acknowledged by Dmitrijs Milajevs and Mehrnoosh Sadrzadeh.
+Matthew Purver is partly supported by ConCreTe: the project ConCreTe acknowledges the financial support of the Future and Emerging Technologies (FET) programme within the Seventh Framework Programme for Research of the European Commission, under FET grant number 611733.
 

### 2016-06-10 figures/interaction-cds.tex

--- 2016-02-27 figures/interaction-cds.tex
@@
     \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-cds}}
-    \caption{\textbf{The effect of context probability estimation and smoothing on SimLex-999.}}
+    \caption{{\bf Effect of PMI variant (\texttt{discr}), smoothing (\texttt{cds}) and frequency weighting (\texttt{freq}) on SimLex-999.} Error bars correspond to a 95\% confidence interval as the value is estimated by averaging over all the values of the omitted parameters: \texttt{neg} and similarity.}
     \label{fig:interaction-cds}

### 2016-06-10 figures/interaction-neg.tex
Pre-submission.
Mentoring comments

@@
     \centerline{\includegraphics[width=1.11\textwidth]{supplement/figures/SimLex999-interaction-neg}}
-    \caption{\textbf{The behaviour of shifted PMI on SimLex-999.}}
+    \caption{\textbf{The behaviour of shifted PMI (SPMI) on SimLex-999.} \texttt{discr=spmi}, \texttt{freq=1} and \texttt{neg=1} corresponds to positive PMI.
+Error bars correspond to a 95\% confidence interval as the value is estimated by averaging over all the values of the omitted parameters: \texttt{cds} and similarity.}
     \label{fig:interaction-neg}

### 2016-06-10 paper.tex
Final changes

@@
 To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset.
-The reason for choosing these is that they are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and in quality by attention to evaluated relations.
+These datasets are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and in quality by attention to evaluated relations \cite{DBLP:journals/corr/MilajevsG16}.
 
